### 2017-06-03 tex/paper_v1.tex
init tex

%% LyX 2.2.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,sigconf]{acmart}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\usepackage{color}
\usepackage{amsmath}
\usepackage{graphicx}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.

\usepackage{booktabs}% For formal tables
\usepackage{float}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}

\usepackage{rotating}
\usepackage{array}
\newcolumntype{L}[1]{>{\vspace{0.5em}\begin{minipage}{#1}\raggedright\let\newline\\
\arraybackslash\hspace{0pt}}m{#1}<{\end{minipage}\vspace{0.5em}}}
\newcolumntype{R}[1]{>{\vspace{0.5em}\begin{minipage}{#1}\raggedleft\let\newline\\
\arraybackslash\hspace{0pt}}m{#1}<{\end{minipage}\vspace{0.5em}}}
\newcolumntype{C}[1]{>{\vspace{0.5em}\begin{minipage}{#1}\centering\let\newline\\
\arraybackslash\hspace{0pt}}m{#1}<{\end{minipage}\vspace{0.5em}}}

\copyrightyear{2017}
\acmYear{2017}
\setcopyright{acmcopyright}
\acmConference{}{}{} 
\acmPrice{15.00} 
\acmDOI{http://dx.doi.org/xxx}
\acmISBN{ACM ISBN xxx}

\clubpenalty=10000 
\widowpenalty = 10000

\makeatother

\usepackage{babel}
\begin{document}
\title{Frame-Transformer Emotion Classification Network}

\author{Jiarui~Gao$^1$}

\affiliation{
\institution{  $^1$School of Computer Science, Shanghai Key Laboratory of Intelligent Information Processing,\\ Fudan University, China}   
}
\email{  jrgao14@fudan.edu.cn}

\begin{abstract}

Emotional content is a key ingredient in user-generated videos.  
However, due to the emotions sparsely expressed in the user-generated video,  it is very difficult to analayze emotions in  videos. In this paper, we propose a new architecture--Frame-Transformer Emotion Classification Network (FT-EC-net) to solve three highly correlated emotion analysis tasks:  emotion recognition, emotion attribution and emotion-oriented summarization. We also contribute a new dataset for emotion attribution task by annotating the ground-truth labels of attribution segments. A comprehensive set of experiments on two datasets demonstrate the effectiveness of our framework.
\end{abstract}
\keywords{Video emotion recognition; video emotion attribution; video emotion-oriented summarization and spatial-transformer network}

\maketitle

\bibliographystyle{ACM-Reference-Format}
\bibliography{security} 
\end{document}

### 2017-06-03 tex/paper_v1.tex
some introduction

@@
 \begin{document}
-\title{Frame-Transformer Emotion Classification Network}
+\title{A Cost-based Approach for Fast Intrusion Detection }
 
@@
 
-Emotional content is a key ingredient in user-generated videos.  
-However, due to the emotions sparsely expressed in the user-generated video,  it is very difficult to analayze emotions in  videos.
-In this paper, we propose a new architecture--Frame-Transformer Emotion Classification Network (FT-EC-net) to solve three highly correlated emotion analysis tasks:  emotion recognition, emotion attribution and emotion-oriented summarization.
-We also contribute a new dataset for emotion attribution task by annotating the ground-truth labels of attribution segments.
-A comprehensive set of experiments on two datasets demonstrate the effectiveness of our framework.
+The aim of Intrusion Detection System(IDS) is to maximize detection accuracy as well as minimize corresponding costs.
+In this paper, I present a cost-based approach utilizing neural network with GPU acceleration for fast intrusion detection.
+In this approach, both computational cost and feature cost are considered, and models are trained with respect to their different protocol types and services.
+Empirical experiments are carried out on off-line benchmark dataset NSL-KDD.
+
 \end{abstract}
-\keywords{Video emotion recognition; video emotion attribution; video emotion-oriented summarization and spatial-transformer network}
+\keywords{Neural network; Intrusion detection; anomaly detection; cost analysis.}
 
 \maketitle
+
+\section{Introduction}
+With the development of computing and Internet technology, Internet has became an important part of our daily life. However, this popularity has also brought security issues. 
+Intrusion Detection Systems(IDSs) are designed to detect attacks, which help discover, determine, and identify unauthorized use, duplication, alteration, and destruction of information systems\cite{mukkamala2005cyber}.
+Specifically, IDSs are able to monitor intrusions and alert network administrators if necessary.
+
+According to the detectable attacks, there are mainly three types of IDSs: misuse-based, anomaly-based, and hybrid\cite{buczak2016survey}.
+Misuse-based IDSs are designed to detect known attacks by comparing signatures of those attacks and those in the database.
+Anomaly-based IDSs have the ability for detecting zero-day attacks. The normal network are modeled and anomalies can be detected when happened.
+
+Also with respect for using environment, IDSs can be used in real-time environment of off-line environment. Off-line IDSs have been studied extensively recently. 
+However, these systems fail to provide real time information, which means they can only detect intrusions after they already happened.
+The challenge for real-time IDSs is the huge cost brought with the detection.
+
+In this paper, the aim is to develop a IDS which can be utilized in real-time environment with high detection accuracy.
+I present a cost-based approach for anomaly intrusion detection.
+The traditional machine learning models are replaced by neural networks, which enable the computational cost to be minimized utilizing GPU acceleration.
+Also, the feature cost is considered, and according to the feature cost theory in \cite{lee2001real}, low level features are utilized with high priority.
+The benchmark dataset NSL-KDD is used for evaluation, which is a new version of dataset KDDCUP'99\cite{cup2007available} and has significant improvements compared with KDDcup99\cite{tavallaee2009detailed}.
+
+The rest of the paper is organized as follows.
+
+\section{Related Work}
+\section{Methodology}
+\section{Experiments}
+\section{Conclusion}
 

### 2017-06-03 baseline.py

@@ -1,8 +1,9 @@
 import numpy as np
 from sklearn import svm  
 from process_data import znormalization
+import time
 
-data = np.load('./feature/tcp_smtp.npz')
+data = np.load('./feature/tcp_finger.npz')
 
 x_train = data['x_train'][:,0:7]
 y_train = data['y_train'].ravel()
@@ -17,5 +18,8 @@ print X_train
 clf = svm.SVC()
 clf.fit(X_train, y_train)
 
+time1 = time.time()
 result = np.round(clf.predict(X_test))
+time2 = time.time()
+print float(time2 - time1) / float(len(y_test))
 print float(sum(result==y_test)) / float(len(y_test))

### 2017-06-03 train_example.py

@@ -3,8 +3,9 @@ import numpy as np
 from tf_utils import weight_variable, bias_variable, dense_to_one_hot, weight_variable_cnn
 from process_data import znormalization
 from shuffle_data import shuffle
+import time
 
-data = np.load('./feature/udp_private.npz')
+data = np.load('./feature/tcp_finger.npz')
 
 x_train = data['x_train'][:,0:7]
 y_train = data['y_train'].ravel()
@@ -69,9 +70,12 @@ for epoch_i in range(n_epochs):
 
         sess.run(optimizer, feed_dict={
             x: batch_xs, y: batch_ys, keep_prob: 0.75})
+    time1 = time.time()
     print('test (%d): ' % epoch_i + str(sess.run(accuracy,feed_dict={x: X_test,y: Y_test,keep_prob: 1.0})))
+    time2 = time.time()
+    print float(time2 - time1) / float(len(y_test))
     # grad_vals = sess.run([g for (g,v) in grads], feed_dict={x: batch_xs, y: batch_ys, keep_prob: 1.0})
     # print 'grad_vals: ', grad_vals
-    theta = sess.run(h_fc1, feed_dict={x: batch_xs, keep_prob: 1.0})
-    print theta
+    # theta = sess.run(h_fc1, feed_dict={x: batch_xs, keep_prob: 1.0})
+    # print theta
     

### 2017-06-04 tex/paper_v1.tex
methodology

@@
 \usepackage{graphicx}
+\usepackage{multirow}
+\usepackage{multicol}
 
@@
 \affiliation{
-\institution{  $^1$School of Computer Science, Shanghai Key Laboratory of Intelligent Information Processing,\\ Fudan University, China}   
+\institution{$^1$School of Computer Science, Shanghai Key Laboratory of Intelligent Information Processing,\\ Fudan University, China}   
 }
-\email{  jrgao14@fudan.edu.cn}
+\email{jrgao14@fudan.edu.cn}
 
@@
 In this paper, I present a cost-based approach utilizing neural network with GPU acceleration for fast intrusion detection.
-In this approach, both computational cost and feature cost are considered, and models are trained with respect to their different protocol types and services.
+In this approach, both computational cost and time cost are considered, and models are trained with respect to their different protocol types and services.
 Empirical experiments are carried out on off-line benchmark dataset NSL-KDD.
@@
 The traditional machine learning models are replaced by neural networks, which enable the computational cost to be minimized utilizing GPU acceleration.
-Also, the feature cost is considered, and according to the feature cost theory in \cite{lee2001real}, low level features are utilized with high priority.
+Also, the time cost is considered, and according to the time cost theory in \cite{lee2001real}, low level features are utilized with high priority.
 The benchmark dataset NSL-KDD is used for evaluation, which is a new version of dataset KDDCUP'99\cite{cup2007available} and has significant improvements compared with KDDcup99\cite{tavallaee2009detailed}.
@@
 The rest of the paper is organized as follows.
+Sec \ref{sec:relatedwork} gives a detailed review of current related work about intrusion detection.
+In Sec \ref{sec:methodology}, the new approach for intrusion detection is introduced.
+The experimental results are reported in Sec \ref{sec:experiment}.
+More future work is presented in Sec \ref{sec:futurework}.
+Finally, a conclusion is drew in Sec \ref{sec:conclusion}.
 
-\section{Related Work}
-\section{Methodology}
-\section{Experiments}
-\section{Conclusion}
+\section{Related Work}\label{sec:relatedwork}
+\subsection{Detection Methodology}
+\subsection{Machine Learning for Intrusion Detection}
+\subsection{Public Datasets}\label{sec:publicdatasets}
+
+\section{Methodology}\label{sec:methodology}
+
+As shown in Fig \ref{fig:overview}, a multi-model detector is presented here.
+
+\begin{figure*}[t]
+\begin{centering}
+\includegraphics[scale=0.5]{img/overview}
+\par\end{centering}
+\caption{\label{fig:overview} An overview of the detection framework including the decision tree(top part) and the neural networks(bottom part).
+The total number of models are calculated on NSL-KDD dataset.}
+\end{figure*}
+
+\subsection{Cost Analysis}
+
+\textbf{Computational Cost.}\quad One of the major challenges in real-time IDSs is the computational cost attached with the system.
+For example, the well-known K-nearest Neighbor Classifier\cite{liao2002use} performs well on off-line datasets, but it is not an appropriate detector in real time.
+Because the
+KNNC calculates the similarity between the new 
+process and each process in the training set to decide the label of the new process. So KNNC is computationally
+expensive when the incoming number of processes is huge.
+
+Traditionally, less features and models with less parameters will lead to low computational cost.
+However, this may also result in lower detection accuracy or higher false alarm rate.
+Different from former approaches, utilizing deep neural networks, the computing tasks can be accelerated on GPU\cite{chetlur2014cudnn}.
+Also, the ability to represent any non-linear function in very few hidden layers and hidden neurons make the computational expense even less.
+
+\noindent\textbf{Time Cost.}\quad It is obvious that the time delay for retrieving features simply from a network packet and extracting information from all former similar connections within a time period are quite different.
+Different from\cite{lee2001real}, the connection based features are utilized according to\cite{lee2001real} in this paper.
+
+\begin{itemize}
+\item Level 1 features are basic features of individual TCP connections.
+\item Level 2 features are content features within a connection suggested by domain knowledge.
+\item Level 3 features are traffic features computed using a two-second time window.
+\end{itemize}
+
+Notice that the Level 3 features require iteration from the entire former two-second packet set, the time cost is extremely high.
+Also, all the Level 3 features for connections coming at the same time can also be computed at the same time.
+
+The lower level features are first used, and if the confidence of the classification is less than a threshold $\theta$, higher level features are extracted and are used combined with other lower level features.
+For example, both Level 1 and Level 2 features are considered after extracting the Level 2 features.
+
+\subsection{Neural Network Detectors}
+
+Packets with different protocol types and different services tend to have different signatures to be malicious. So neural network models are trained for each protocol type and service respectively.
+Thus for each new connection, its protocol type and service decides which detector to use. This model selection framework can be modeled by a decision tree.
+
+Neural network models with only one hidden layer is utilized in this paper, and the following experiments proves their capability for intrusion detection with such simple architectures.
+
+\section{Experiments}\label{sec:experiment}
+\subsection{Dataset}
+As mentioned in Sec \ref{sec:publicdatasets}, NSL-KDD dataset consists of the selected records of the KDDCUP'99 dataset, which is more challenging to detect compared with the original widely used benchmark KDDCUP'99 dataset.
+The NLS-KDD dataset solves the issues of models trained on KDDCUP'99 dataset, which have high seemingly accuracy but actually poor capability of anomaly detection.
+
+All the features in NSL-KDD dataset are considered in this paper except the additional feature: detection difficulty, which is generalized by statistical analysis for the KDDCUP'99 dataset\cite{tavallaee2009detailed}.
+Totally, there are $61$ different TCP services, $5$ different UDP services and $6$ different ICMP services.
+
+\subsection{Parameter setting}
+All the code is implemented in Python utilizing deep learning framework Tensorflow, and the neural network models are trained on one GPU GeForce GTX TITAN X for $5000$ epochs with early stop policy.
+All the neural networks consist of $1$ hidden layer, and the number of hidden neurons are set specifically for every model.
+The initial learning rate is $\eta = 0.0001$ and dropout ratio is $0.75$.
+Finally, a softmax layer with two output values is utilized to calculate loss and Adam\cite{kingma2014adam} is used to accelerate learning.
+
+\subsection{Baseline}
+Support Vector Machine(SVM) is utilized as a baseline method for each model respectively.
+The code are implemented in Python on Scikit-learn Library.
+And the following baseline results are evaluated on the same server with the proposed approach without GPU support for SVM method.
+
+\subsection{Detection Results}
+Due to the coming deadline issue, I have only finished part of the experiments.
+
+\textbf{Detection Accuracy.}
+Tab \ref{tab:detection-accuracy} demonstrates the detection accuracy for each level of features.
+And apart from the over all accuracy, I take three representative protocol type and service(TCP finger/UDP domain\_u/ICMP eco\_i) as examples.
+
+Observed from Tab \ref{tab:detection-accuracy}, we can see that SVM models and neural network models perform nearly the same on most of the detections.
+But neural network models demonstrate a good property that as the level of features get higher, the accuracies never decay; while the SVM method present less stability.
+
+Also, we can observe that the decision tree idea that to detect different protocol types and service with different models is quite reasonable.
+In Tab \ref{tab:detection-accuracy}, huge accuracy improvement has been made thanks to this separation.
+
+\begin{table*}
+
+\caption{\label{tab:detection-accuracy}Detection Accuracy Results.}
+\centering{}
+\begin{tabular}{ccccc}
+
+\hline 
+Methods/Features & Over all & TCP finger & UDP domain\_u & ICMP eco\_i \tabularnewline
+\hline
+\textbf{Level 1 Features} \tabularnewline
+SVM & $78.20\%$ & $99.26\%$ & $99.33\%$ & $94.27\%$ \tabularnewline
+Ours & $77.26\%$ & $99.26\%$ & $99.33\%$ & $94.27\%$\tabularnewline
+\hline
+
+\textbf{Level 2 Features} \tabularnewline
+
+SVM & $81.39\%$ & $97.06\%$ & $99.55\%$ & $94.27\%$\tabularnewline
+Ours & $80.67\%$ & $99.26\%$ & $99.78\%$ & $94.27\%$\tabularnewline
+\hline
+
+\textbf{Level 3 Features} \tabularnewline
+
+SVM & $80.57\%$ & $99.26\%$ & $99.78\%$ & $98.09\%$\tabularnewline
+Ours & $76.24\%$ & $99.26\%$ & $99.78\%$ & $98.89\%$\tabularnewline
+\hline
+\end{tabular}
+\end{table*}
+
+\textbf{Cost Analysis.}
+Tab \ref{tab:cost} demonstrates the \textbf{computational cost} for each level of features.
+The same as former experiments, three representative protocol type and service are selected.
+Notice here I report the average time for computing single one packet feature item.
+
+It can be noticed that significant improvement have been on computational cost utilizing neural network models, which is quite important in real time detection ability for the IDSs.
+
+Also, the \textbf{time cost} is considered.
+Each new packet are first detected according to their Level 1 features.
+If the confidence of the classification, which is the larger value of the two output neurons is less than $\theta=0.8$, than the higher features are extracted and higher level models are used.
+In the worst case, the packet will eventually get its label through Level 3 models. And more additional computational cost will also be spent.
+
+The total cost is the sum of computational cost and time cost, which is much more efficient compared with simply using Level 3 features for all the packets.
+
+\begin{table*}
+
+\caption{\label{tab:cost}Computational Cost Results.}
+\centering{}
+\begin{tabular}{ccccc}
+
+\hline 
+Methods/Features & Over all & TCP finger & UDP domain\_u & ICMP eco\_i \tabularnewline
+\hline
+\textbf{Level 1 Features} \tabularnewline
+SVM & $4.2*10^{-4}s$ & $4.4*10^{-6}s$ & $9.2*10^{-7}s$ & $5.7*10^{-7}s$ \tabularnewline
+Ours & $5.4*10^{-8}s$ & $2.7*10^{-6}s$ & $4.3*10^{-7}s$ & $1.4*10^{-6}s$\tabularnewline
+\hline
+
+\textbf{Level 2 Features} \tabularnewline
+
+SVM & $5.9*10^{-4}s$ & $7.3*10^{-6}s$ & $1.3*10^{-6}s$ & $1.3*10^{-6}s$\tabularnewline
+Ours & $7.0*10^{-8}s$ & $2.7*10^{-6}s$ & $4.6*10^{-7}s$ & $1.4*10^{-6}s$\tabularnewline
+\hline
+
+\textbf{Level 3 Features} \tabularnewline
+
+SVM & $2.3*10^{-4}s$ & $7.2*10^{-6}s$ & $4.1*10^{-6}s$ & $6.2*10^{-6}s$\tabularnewline
+Ours & $1.0*10^{-7}s$ & $2.8*10^{-6}s$ & $5.2*10^{-7}s$ & $1.5*10^{-6}s$\tabularnewline
+\hline
+\end{tabular}
+\end{table*}
+
+\section{Future Work}\label{sec:futurework}
+
+\section{Conclusion}\label{sec:conclusion}
 

### 2017-06-04 baseline_all.py

@@ -3,12 +3,13 @@ from sklearn import svm
 from process_data import znormalization
 import time
 
-data = np.load('./feature/tcp_finger.npz')
+train = np.load('./feature/train.npz')
+test = np.load('./feature/test.npz')
 
-x_train = data['x_train'][:,0:7]
-y_train = data['y_train'].ravel()
-x_test = data['x_test'][:,0:7]
-y_test = data['y_test'].ravel()
+x_train = train['feature'][:,0:7]
+y_train = train['label_2'].ravel()
+x_test = test['feature'][:,0:7]
+y_test = test['label_2'].ravel()
 
 X_train = znormalization(x_train)
 X_test = znormalization(x_test)

### 2017-06-04 split_data.py

@@ -10,12 +10,8 @@ def split_data(url, tcp_finger, label_2):
 	while line:
 		line = line.split(',')
 		temp = str(line[1]) + '_' + str(line[2]) 
-
-		# if package.has_key(temp):			
-		# 	package[temp] = package[temp] + 1
-		# else:
-		# 	package[temp] = 1
-		if temp == 'tcp_smtp':
+		
+		if temp == 'icmp_eco_i':
 			line[3] = flag[line[3]]
 			tcp_finger[i,0] = line[0]
 			tcp_finger[i,1:] = line[3:41]
@@ -30,13 +26,13 @@ def split_data(url, tcp_finger, label_2):
 
 if __name__ == '__main__':
 	
-	tcp_finger_train = np.zeros([7313, 39])
-	label_2_train = np.zeros([1, 7313])
+	tcp_finger_train = np.zeros([4586, 39])
+	label_2_train = np.zeros([1, 4586])
 	url = './NSL_KDD/KDDTrain+.txt'
 	tcp_finger_train, label_2_train = split_data(url, tcp_finger_train, label_2_train)
-	tcp_finger_test = np.zeros([934, 39])
-	label_2_test = np.zeros([1, 934])
+	tcp_finger_test = np.zeros([262, 39])
+	label_2_test = np.zeros([1, 262])
 	url = './NSL_KDD/KDDTest+.txt'
 	tcp_finger_test, label_2_test = split_data(url, tcp_finger_test, label_2_test)
 	
-	np.savez('./feature/tcp_smtp.npz', x_train=tcp_finger_train, x_test=tcp_finger_test, y_train=label_2_train, y_test=label_2_test)
+	np.savez('./feature/icmp_eco_i.npz', x_train=tcp_finger_train, x_test=tcp_finger_test, y_train=label_2_train, y_test=label_2_test)

### 2017-06-04 train_nn.py

@@ -1,6 +1,7 @@
 import tensorflow as tf
 import numpy as np
 from tf_utils import weight_variable, bias_variable, dense_to_one_hot, weight_variable_cnn
+import time
 
 train = np.load('./feature/train.npz')
 test = np.load('./feature/test.npz')
@@ -65,6 +66,9 @@ for epoch_i in range(n_epochs):
 
         sess.run(optimizer, feed_dict={
             x: batch_xs, y: batch_ys, keep_prob: 0.75})
+    time1 = time.time()
     print('test (%d): ' % epoch_i + str(sess.run(accuracy,feed_dict={x: X_test,y: Y_test,keep_prob: 1.0})))
-    grad_vals = sess.run([g for (g,v) in grads], feed_dict={x: batch_xs, y: batch_ys, keep_prob: 1.0})
-    print 'grad_vals: ', grad_vals
+    time2 = time.time()
+    print float(time2 - time1) / float(len(y_test))
+    # grad_vals = sess.run([g for (g,v) in grads], feed_dict={x: batch_xs, y: batch_ys, keep_prob: 1.0})
+    # print 'grad_vals: ', grad_vals

### 2017-06-04 tex/paper_v1.tex
train example

@@
 \subsection{Detection Methodology}
+
 \subsection{Machine Learning for Intrusion Detection}
+
 \subsection{Public Datasets}\label{sec:publicdatasets}
@@
 \section{Future Work}\label{sec:futurework}
+As mentioned in Sec \ref{sec:experiment}, due to the coming deadline, some of the experiments are not completely finished.
+
+The future work for this paper is listed as follows:
+\begin{itemize}
+\item Calculate the average performance for all the models, not for only some examples.
+\item Measure the specific improvement made by distinguishing different level of features quantitatively, such as calculate the exact cost saved for detecting some packets.
+\end{itemize}
+
+There are also some practical need to be solved for further implementation:
+\begin{itemize}
+\item There are some protocol type and service with very few training data, such as TCP pm\_dump, UDP tftp\_u and ICMP urh\_i etc.
+This issue will make it impossible to train a neural network model.
+Maybe some signature-based technique are needed here.
+\item It will cost too much time to train and tune parameters for every model, specifically $72$ models in NSL-KDD dataset. But currently I just train the example models manually.
+\end{itemize}
 

### 2017-06-04 shuffle_data.py

@@ -1,12 +1,12 @@
 import numpy as np
 import random
 
-def shuffle(x_train, y_train, num):
+def shuffle(x_train, y_train, num, opt):
 
 	x = np.linspace(0, num - 1, num)
 	random.shuffle(x)
 
-	X_train = np.zeros([num, 7])
+	X_train = np.zeros([num, opt])
 	Y_train = np.zeros((num,), dtype=np.int)
 
 	for i in range(num):

### 2017-06-04 train_example.py

@@ -6,10 +6,11 @@ from shuffle_data import shuffle
 import time
 
 data = np.load('./feature/tcp_finger.npz')
+opt = 39
 
-x_train = data['x_train'][:,0:7]
+x_train = data['x_train'][:,0:opt]
 y_train = data['y_train'].ravel()
-x_test = data['x_test'][:,0:7]
+x_test = data['x_test'][:,0:opt]
 y_test = data['y_test'].ravel()
 
 X_train = znormalization(x_train)
@@ -17,19 +18,19 @@ X_test = znormalization(x_test)
 X_train = np.nan_to_num(X_train)
 X_test = np.nan_to_num(X_test)
 
-[X_train, y_train] = shuffle(X_train, y_train, x_train.shape[0])
+[X_train, y_train] = shuffle(X_train, y_train, x_train.shape[0], opt)
 Y_train = dense_to_one_hot(y_train, n_classes=2)
 Y_test = dense_to_one_hot(y_test, n_classes=2)
 
-x = tf.placeholder(tf.float32, [None, 7])
+x = tf.placeholder(tf.float32, [None, opt])
 y = tf.placeholder(tf.float32,[None, 2])
 keep_prob = tf.placeholder(tf.float32)
 
-W_fc1 = weight_variable_cnn([7, 5])
-b_fc1 = bias_variable([5])
+W_fc1 = weight_variable_cnn([opt, 8])
+b_fc1 = bias_variable([8])
 h_fc1 = tf.nn.tanh(tf.matmul(x, W_fc1) + b_fc1)
 h_fc1_drop = tf.nn.dropout(h_fc1, keep_prob)
-W_fc2 = weight_variable_cnn([5, 2])
+W_fc2 = weight_variable_cnn([8, 2])
 b_fc2 = bias_variable([2])
 h_fc2 = tf.nn.tanh(tf.matmul(h_fc1_drop, W_fc2) + b_fc2)
 
@@ -53,6 +54,7 @@ train_size = x_train.shape[0]
 
 indices = np.linspace(0, train_size - 1, iter_per_epoch)
 indices = indices.astype('int')
+time_sum = 0
 
 for epoch_i in range(n_epochs):
     for iter_i in range(iter_per_epoch - 1):
@@ -64,7 +66,7 @@ for epoch_i in range(n_epochs):
                             feed_dict={
                                 x: batch_xs,
                                 y: batch_ys,
-                                keep_prob: 1.0
+                                keep_prob: 0.75
                             })
[…]

### 2017-06-04 train_nn.py

@@ -1,28 +1,31 @@
 import tensorflow as tf
 import numpy as np
 from tf_utils import weight_variable, bias_variable, dense_to_one_hot, weight_variable_cnn
+from shuffle_data import shuffle
 import time
 
 train = np.load('./feature/train.npz')
 test = np.load('./feature/test.npz')
+opt = 41
 
-X_train = train['feature'][:,0:9]
+X_train = train['feature'][:,0:opt]
 label_2 = train['label_2']
 label_5 = train['label_5']
 label_23 = train['label_23']
 y_train = label_2.ravel()
-X_test = test['feature'][:,0:9]
+X_test = test['feature'][:,0:opt]
 test_l = test['label_2']
 y_test = test_l.ravel()
 
+[X_train, y_train] = shuffle(X_train, y_train, X_train.shape[0],opt)
 Y_train = dense_to_one_hot(y_train, n_classes=2)
 Y_test = dense_to_one_hot(y_test, n_classes=2)
 
-x = tf.placeholder(tf.float32, [None, 9])
+x = tf.placeholder(tf.float32,[None, opt])
 y = tf.placeholder(tf.float32,[None, 2])
 keep_prob = tf.placeholder(tf.float32)
 
-W_fc1 = weight_variable([9, 5])
+W_fc1 = weight_variable([opt, 5])
 b_fc1 = bias_variable([5])
 h_fc1 = tf.nn.tanh(tf.matmul(x, W_fc1) + b_fc1)
 W_fc2 = weight_variable([5, 2])
@@ -43,9 +46,10 @@ grads = opt.compute_gradients(cross_entropy, [W_fc1])
 sess = tf.Session()
 sess.run(tf.initialize_all_variables())
 
-iter_per_epoch = 60
+iter_per_epoch = 10
 n_epochs = 1000
 train_size = 125973
+time_sum = 0
 
 indices = np.linspace(0, train_size - 1, iter_per_epoch)
 indices = indices.astype('int')
@@ -60,7 +64,7 @@ for epoch_i in range(n_epochs):
                             feed_dict={
                                 x: batch_xs,
                                 y: batch_ys,
-                                keep_prob: 1.0
+                                keep_prob: 0.75
                             })
             print('Iteration: ' + str(iter_i) + ' Loss: ' + str(loss))
 
@@ -69,6 +73,7 @@ for epoch_i in range(n_epochs):
     time1 = time.time()
[…]

### 2017-06-05 tex/paper_v1.tex
add false alarm

@@
 According to the detectable attacks, there are mainly three types of IDSs: misuse-based, anomaly-based, and hybrid\cite{buczak2016survey}.
-Misuse-based IDSs are designed to detect known attacks by comparing signatures of those attacks and those in the database.
-Anomaly-based IDSs have the ability for detecting zero-day attacks. The normal network are modeled and anomalies can be detected when happened.
+Misuse-based IDSs, which are also called signature-based IDSs are designed to detect known attacks by comparing new packets and the signatures in the database.
+Anomaly-based IDSs aims at modeling the normal network, and anomalies can be detected when happened.
+An attractive property of the anomaly-based IDSs is that they have the ability for detecting zero-day attacks.
 
-Also with respect for using environment, IDSs can be used in real-time environment of off-line environment. Off-line IDSs have been studied extensively recently. 
-However, these systems fail to provide real time information, which means they can only detect intrusions after they already happened.
-The challenge for real-time IDSs is the huge cost brought with the detection.
+Also with respect for using environment, IDSs can be used in real-time environment or off-line environment.
+Off-line IDSs have been studied extensively recently especially with the support of data mining and machine learning techniques, such as K-means\cite{lin2015cann} and ANN\cite{ingre2015performance} etc.
+And excellent detection results with high accuracies and low false alarm rates are demonstrated.
+For detailed introduction for these machine learning techniques, the survey\cite{buczak2016survey} is recommended.
 
-In this paper, the aim is to develop a IDS which can be utilized in real-time environment with high detection accuracy.
+However, these systems fail to provide real time information, which means they can only detect intrusions after they already happened for a while.
+However, it's obvious that as the complexity of features increase, the detection accuracy will also make an improvement.
+So a balance need to be maintained between accuracy and efficiency.
+
+In this paper, the aim is to develop an IDS which can be utilized in real-time environment with high detection accuracy and low cost.
 I present a cost-based approach for anomaly intrusion detection.
@@
 Also, the time cost is considered, and according to the time cost theory in \cite{lee2001real}, low level features are utilized with high priority.
-The benchmark dataset NSL-KDD is used for evaluation, which is a new version of dataset KDDCUP'99\cite{cup2007available} and has significant improvements compared with KDDcup99\cite{tavallaee2009detailed}.
+The benchmark dataset NSL-KDD is used for evaluation, which is a new version of dataset KDD Cup 1999\cite{cup2007available} and has significant improvements compared with KDD Cup 1999\cite{tavallaee2009detailed}.
 
@@
 \subsection{Detection Methodology}
+Basically, there are three types of intrusion detection techniques: misuse-based, anomaly-based, and hybrid\cite{buczak2016survey}. Hybrid techniques are a combination for the two former techniques.
 
-\subsection{Machine Learning for Intrusion Detection}
+\subsubsection{Misuse-based Intrusion Detection}
+The misuse-based intrusion detection is also known as signature-based or knowledge-based intrusion detection.
+A signature is a pattern or string that corresponds to a known attack or threat\cite{liao2013intrusion}.
+So in the misuse-based IDS, the process for coming packets is to compare them with the known signatures for recognizing possible intrusions.
+
+The advantages of misuse-based method is that the misuse-based method is effective for detecting known type of attacks free from false alarms.
+However, the disadvantages are that it's usually hard to keep the signature database up to date.
+Also, the technique is incapable in detecting zero-day attacks or any attacks whose signatures are not included in the database.
+
+\subsubsection{Anomaly-based Intrusion Detection}
+An anomaly is a deviation to a known behavior, and profiles represent the normal or expected behaviors derived from monitoring regular activities, network connections, hosts or users over a period of time\cite{liao2013intrusion}.
+The anomaly-based techniques aims at modeling normal network status, and new packets are compared with the normal normal status to distinguish an attack.
+
+The advantages of anomaly-based method is that they have the ability to recognize zero-day attacks.
+Another advantage is that unlike the misuse-based method, the profiles of normal activity are customized for every system, application, or network, thereby making it difficult for attackers to know which activities they can carry out undetected\cite{buczak2016survey}.
+The main disadvantage of anomaly-based techniques is the it may present high false alarm rates, since every behavior that has not happened before has the potential risk to be considered as a intrusion.
+
+\subsubsection{Hybrid Intrusion Detection}
+Hybrid techniques combine the former two types of methods.
+They are implemented aiming at decrease the false alarm rate as well as detecting zero-day attacks.
+
+\subsection{Feature Selection}
+The reduction of features and feature selection are very important in increasing the efficiency of the detection.
+
+This work aims at reduce the features used for misuse-based techniques\cite{chebrolu2005feature}, since the comparison between the whole packet and all the signatures can be redundant.
+And useful feature selection algorithms are proposed.
+Also, the features on one specific dataset KDD Cup 1999 are analyzed by comparing the relevance between each features and information gain is employed to find the most discriminating features for each class\cite{kayacik2005selecting}.
+
+Unsupervised machine learning techniques such as PCA\cite{liu2007hierarchical}\cite{lakhina2010feature} and K-means\cite{kumar2013k} are employed for feature selection.
+And all of these methods demonstrates good performance in feature selection.
+
+However, these feature selection method ignore the time cost brought by the extraction process, so the selected features may bring severe time delay.
+In the cost-based approach presented in this paper, the cost factors are considerer, and a balance between cost and accuracy is maintained.
+
+\subsection{Machine Learning Approaches}
+In this section present a brief introduce of the utilization of machine learning techniques in intrusion detection.
+Specific machine learning algorithm is beyond the scope of this paper, and this book\cite{bishop2006pattern} is highly recommended for more information.
+
+\subsubsection{Supervised Learning}
+Supervised learning can be divided into generative models and deterministic models, and both contain plenty of proposed models.
+Some of the popular supervised learning methods are listed as follows: Artificial Neural Network, Bayesian Network, Decision Tree, Genetic Algorithms, Hidden Markov Models, Naive Bayes, Support Vector Machine etc.
+
+Nearly all the former techniques in supervised learning are used in intrusion detection\cite{ingre2015performance}\cite{sommer2010outside}\cite{qiao2002anomaly}.
+Both the computational complexity and concrete introduction of the former techniques can be found in this work\cite{buczak2016survey}.
+
+\subsubsection{Unsupervised Learning}
+One of the most frequently used techniques is \textbf{clustering}.  
+It is an unsupervised learning aims at clustering the data with some same property together.
+The main advantage of clustering is that it makes the labeling work not necessary.
+Specifically, for intrusion detection, the system can learn from audit data without requiring the network administrator to provide the attacks information.
+
+There are many clustering method that demonstrates an excellent performance in detection intrusion experiments\cite{hendry2008intrusion}\cite{lin2015cann}\cite{kumar2013k}\cite{tsai2010triangle}.
+K-means, K-NN and etc are popular unsupervised machine learning approaches.
+Also, some work combine them together and better results are demonstrated\cite{lin2015cann}.
+However, as mentioned in the mentioned work, feature selection and reduction are urgently needed in methods like K-NN, because computing the similarities between high dimensions of features are expensive.
+
+\subsubsection{Ensemble Learning}
+Actually, the ensemble learning approaches do not belong to supervised or unsupervised learning.
+Usually, the idea of ensemble learning is to use multiple weak models to build a strong model, since some classification tasks may be difficult for one classifier.
+And complex models with lots of parameters always tend to over fit on the training data.
+Bagging and boosting are frequently used approaches in ensemble learning, \cite{dietterich2000experimental} gives a good example for utilizing ensemble learning methods in decision tree models.
+
+\textbf{Bagging}\cite{breiman1996bagging} predictors is a method for generating multiple versions of a single model and using these to get an aggregated predictor.
+The aggregation averages over all the versions of models when predicting a result by majority voting.
+\textbf{Boosting}\cite{freund1995desicion} basically concentrates more the mis-classified data in the modeling process.
+Adaptive Boosting (AdaBoost)\cite{polikar2006ensemble} is one of the most popular algorithms in boosting.
+The \textbf{Random Forest}\cite{breiman2001random} another method that combines the decision trees and ensemble learning. The so-called forest is composed of many decision trees.
+
+Ensemble learning is extensively used in intrusion detection\cite{zhang2008random}\cite{mukkamala2005intrusion}. The single model can be nearly all kinds of previous mentioned machine learning models.
 
 \subsection{Public Datasets}\label{sec:publicdatasets}
+
+\subsubsection{DARPA 1998 and DARPA 1999 Datasets}
+One of the most commonly used datasets are the Defense Advanced Research Projects Agency (DARPA)
+1998 and DARPA 1999 datasets\cite{lippmann2000evaluating}\cite{lippmann20001999}.
+Both of the datasets are created by the Cyber Systems and Technology Group of the Massachusetts Institute of Technology Lincoln Laboratory (MIT/LL).
+The datasets contain both network and operating system data.
+Totally, seven weeks of training data and two weeks of test data are collected, and attack simulations are organized during both of the periods.
+
+\subsubsection{KDD Cup 1999 Dataset}
+KDD Cup 1999 dataset\cite{tavallaee2009detailed} is one of the most widely used intrusion detection datasets, which is created for the KDD Cup challenge in 1999.
+The dataset is based on DARPA 1998 TCP/IP dataset and some basic features are extracted, as well as some more advanced features like some content features within a connection and traffic features computed using a two-second time window.
+Totally, $41$ features are extracted for a single connection.
+
+\subsubsection{NSL-KDD Dataset}
+As suggested in \cite{tavallaee2009detailed}, the original KDD Cup 1999 dataset has two important issues which highly affects the performance of evaluated systems, and results in a very poor evaluation of anomaly detection approaches.
+The NSL-KDD dataset consists of selected records of the complete KDD data set and free from the mentioned shortcomings in \cite{tavallaee2009detailed}.
+
+\subsubsection{ADFA Intrusion Detection Datasets}
+The ADFA Intrusion Detection Datasets cover both Linux and Windows\cite{creech2013generation}. Different from former introduced datasets, ADFA contains raw system call traces. 
+A new host-based anomaly intrusion detection methodology is evaluated on ADFD\cite{creech2014semantic}, which utilizing discontiguous system call patterns to increase detection rates whilst reducing false alarm rates.
+Also, excellent results are demonstrated.
 
@@
 As shown in Fig \ref{fig:overview}, a multi-model detector is presented here.
+Based on a decision tree structure, different models are used for every kind of packets with different protocol types and services.
+And neural network models are trained for each level of features respectively.
 
@@
 \begin{centering}
-\includegraphics[scale=0.5]{img/overview}
+\includegraphics[scale=0.55]{img/overview}
 \par\end{centering}
@@
 
-\textbf{Computational Cost.}\quad One of the major challenges in real-time IDSs is the computational cost attached with the system.
+\subsubsection{Computational Cost}
+One of the major challenges in real-time IDSs is the computational cost attached with the system.
 For example, the well-known K-nearest Neighbor Classifier\cite{liao2002use} performs well on off-line datasets, but it is not an appropriate detector in real time.
@@
 KNNC calculates the similarity between the new 
-process and each process in the training set to decide the label of the new process. So KNNC is computationally
-expensive when the incoming number of processes is huge.
+packet and each packet in the training set to decide the label of the new packet. So KNNC is computationally
+expensive when the incoming number of packets is huge, causing the system to be overloaded.
 
-Traditionally, less features and models with less parameters will lead to low computational cost.
+Traditionally, less features numbers and models with less parameters will lead to low computational cost.
 However, this may also result in lower detection accuracy or higher false alarm rate.
@@
 
-\noindent\textbf{Time Cost.}\quad It is obvious that the time delay for retrieving features simply from a network packet and extracting information from all former similar connections within a time period are quite different.
+\subsubsection{Time Cost}
+It is obvious that the time delay for retrieving features simply from a network packet and extracting information from all former similar connections within a time period are quite different.
 Different from\cite{lee2001real}, the connection based features are utilized according to\cite{lee2001real} in this paper.
@@
 
-Notice that the Level 3 features require iteration from the entire former two-second packet set, the time cost is extremely high.
+Notice that the Level 3 features require iteration from the entire former two-second packet set, the time cost is extremely high compares with the lower level of features.
 Also, all the Level 3 features for connections coming at the same time can also be computed at the same time.
 
-The lower level features are first used, and if the confidence of the classification is less than a threshold $\theta$, higher level features are extracted and are used combined with other lower level features.
+The process of utilizing different levels of features is:
+\begin{itemize}
+\item The lower level features are first used;
+\item If the confidence of the classification is less than a threshold $\theta$, higher level features are extracted and are used combined with other lower level features;
+\item If the extracted feature level is already $3$, then the eventual detection result is made without confidence calculating.
+\end{itemize}
 For example, both Level 1 and Level 2 features are considered after extracting the Level 2 features.
+
+\subsection{Decision Tree Model}
+
+Packets with different protocol types and different services tend to have different signatures to be malicious.
+Thus different detectors should be trained, and for each new packet, its protocol type and service decides which detector to use. This model selection framework can be modeled by a decision tree.
+
+As shown in Fig \ref{fig:overview}, the decision has very simple architecture in the proposed approach.
 
@@
 
-Packets with different protocol types and different services tend to have different signatures to be malicious. So neural network models are trained for each protocol type and service respectively.
-Thus for each new connection, its protocol type and service decides which detector to use. This model selection framework can be modeled by a decision tree.
+Neural network models are at the bottom layer for the detection process, they trained for each protocol type and service respectively.
+Actually due to the less complexity for packets detection, neural network models perform nearly the same as traditional classifiers.
+The main reason of utilizing neural network models in this paper is the excellent CPU acceleration support for deep learning libraries, which will reduce the computational cost in some extent.
 
@@
 \subsection{Dataset}
-As mentioned in Sec \ref{sec:publicdatasets}, NSL-KDD dataset consists of the selected records of the KDDCUP'99 dataset, which is more challenging to detect compared with the original widely used benchmark KDDCUP'99 dataset.
-The NLS-KDD dataset solves the issues of models trained on KDDCUP'99 dataset, which have high seemingly accuracy but actually poor capability of anomaly detection.
+As mentioned in Sec \ref{sec:publicdatasets}, NSL-KDD dataset consists of the selected records of the KDD Cup 1999 dataset, which is more challenging to detect compared with the original widely used benchmark KDD Cup 1999 dataset.
+The NLS-KDD dataset solves the issues of models trained on KDD Cup 1999 dataset, which have high seemingly accuracy but actually poor capability of anomaly detection.
 
-All the features in NSL-KDD dataset are considered in this paper except the additional feature: detection difficulty, which is generalized by statistical analysis for the KDDCUP'99 dataset\cite{tavallaee2009detailed}.
+All the features in NSL-KDD dataset are considered in this paper except the additional feature: detection difficulty, which is generalized by statistical analysis for the KDD Cup 1999 dataset\cite{tavallaee2009detailed}.
 Totally, there are $61$ different TCP services, $5$ different UDP services and $6$ different ICMP services.
 
-\subsection{Parameter setting}
-All the code is implemented in Python utilizing deep learning framework Tensorflow, and the neural network models are trained on one GPU GeForce GTX TITAN X for $5000$ epochs with early stop policy.
+\subsection{Parameter Setting}
+The data preprocessing method z-normalization is employed.
+All the code for the neural network models is implemented in Python utilizing deep learning framework Tensorflow, and the neural network models are trained on one GPU GeForce GTX TITAN X for $5000$ epochs with early stop policy.
 All the neural networks consist of $1$ hidden layer, and the number of hidden neurons are set specifically for every model.
-The initial learning rate is $\eta = 0.0001$ and dropout ratio is $0.75$.
-Finally, a softmax layer with two output values is utilized to calculate loss and Adam\cite{kingma2014adam} is used to accelerate learning.
+The initial learning rate is $\eta = 0.0001$ and dropout ratio is $0.75$ to avoid over fitting.
+Finally, a softmax layer is utilized to calculate loss and Adam\cite{kingma2014adam} is employed to accelerate learning.
+The prediction results of the models are the values of the two output neurons.
 
 \subsection{Baseline}
-Support Vector Machine(SVM) is utilized as a baseline method for each model respectively.
+Support Vector Machine(SVM) is employed as a baseline method for each model respectively.
 The code are implemented in Python on Scikit-learn Library.
@@
 
-\textbf{Detection Accuracy.}
+\subsubsection{Detection Accuracy.}
 Tab \ref{tab:detection-accuracy} demonstrates the detection accuracy for each level of features.
@@
 Observed from Tab \ref{tab:detection-accuracy}, we can see that SVM models and neural network models perform nearly the same on most of the detections.
-But neural network models demonstrate a good property that as the level of features get higher, the accuracies never decay; while the SVM method present less stability.
+But neural network models demonstrate a good property on the three examples that as the level of features get higher, the accuracies never decay; while the SVM method present less stability.
+Actually, this property is quite important in the proposed approach, because the accuracy decay on higher feature level will result in some eventual detection results to be wrong.
+Since the results for packets that cannot be classified confidently by the lower feature level models are decided finally by the higher feature level models.
+Also, lots of time cost will be wasted for no improvement in detection accuracy.
 
@@
 SVM & $78.20\%$ & $99.26\%$ & $99.33\%$ & $94.27\%$ \tabularnewline
-Ours & $77.26\%$ & $99.26\%$ & $99.33\%$ & $94.27\%$\tabularnewline
+Ours & $79.16\%$ & $99.26\%$ & $99.33\%$ & $94.27\%$\tabularnewline
 \hline
@@
 
-\textbf{Cost Analysis.}
+\subsubsection{False Alarm Rates.}
+Tab \ref{tab:detection-false-alarm} demonstrates the false alarm rates for each level of features. As mentioned before, three representative protocol type and service are presented.
+
+As observed, the false alarm rates decay as the increasing level of features.
+
+\begin{table*}
+
+\caption{\label{tab:detection-false-alarm}Detection False Alarm Rates.}
+\centering{}
+\begin{tabular}{ccccc}
+
+\hline 
+Methods/Features & Over all & TCP finger & UDP domain\_u & ICMP eco\_i \tabularnewline
+\hline
+\textbf{Level 1 Features} \tabularnewline
+SVM & $3.86\%$ & $0.00\%$ & $0.67\%$ & $57.69\%$ \tabularnewline
+Ours & $4.40\%$ & $99.26\%$ & $99.33\%$ & $94.27\%$\tabularnewline
+\hline
+
+\textbf{Level 2 Features} \tabularnewline
+
+SVM & $81.39\%$ & $0.00\%$ & $0.45\%$ & $57.69\%$\tabularnewline
+Ours & $3.49\%$ & $99.26\%$ & $99.78\%$ & $94.27\%$\tabularnewline
+\hline
+
+\textbf{Level 3 Features} \tabularnewline
+
+SVM & $2.19\%$ & $0.00\%$ & $0.00\%$ & $19.23\%$\tabularnewline
+Ours & $6.64\%$ & $99.26\%$ & $99.78\%$ & $98.89\%$\tabularnewline
+\hline
+\end{tabular}
+\end{table*}
+
+\subsubsection{Cost Analysis.}
 Tab \ref{tab:cost} demonstrates the \textbf{computational cost} for each level of features.
@@
 
-It can be noticed that significant improvement have been on computational cost utilizing neural network models, which is quite important in real time detection ability for the IDSs.
+Thanks to CPU acceleration, it can be noticed that significant improvement have been made on computational cost utilizing neural network models, which is quite important in real time detection for the IDSs.
+Also the number of neurons in the hidden layer is reduced as small as possible, which also save the computational cost.
 
-Also, the \textbf{time cost} is considered.
-Each new packet are first detected according to their Level 1 features.
+Also, \textbf{time cost} is considered.
+Every new packet are first detected according to their Level 1 features.
 If the confidence of the classification, which is the larger value of the two output neurons is less than $\theta=0.8$, than the higher features are extracted and higher level models are used.
@@
 
-The total cost is the sum of computational cost and time cost, which is much more efficient compared with simply using Level 3 features for all the packets.
+The total cost is the sum of computational cost and time cost.
+The proposed approach is much more efficient compared with simply using Level 3 features for all the packets, and there is almost no decay of detection accuracy.
 
@@
 \section{Future Work}\label{sec:futurework}
+\subsection{More Experiments}
 As mentioned in Sec \ref{sec:experiment}, due to the coming deadline, some of the experiments are not completely finished.
@@
 \item Measure the specific improvement made by distinguishing different level of features quantitatively, such as calculate the exact cost saved for detecting some packets.
+\item Try more specific detection results than just normal and anomaly classification. Actually, the NSL-KDD dataset provides the labels of the specific attack types for each connection.
 \end{itemize}
 
-There are also some practical need to be solved for further implementation:
+\subsection{More Issues}
+There are also some practical issues need to be solved for further implementation:
 \begin{itemize}
@@
 \item It will cost too much time to train and tune parameters for every model, specifically $72$ models in NSL-KDD dataset. But currently I just train the example models manually.
+\item Utilizing the features in NSL-KDD makes the detection in this paper to be connection based, which means that the intrusion can only be detected after all the packages in one connection have arrived.
+Actually, as suggested in\cite{lee2001real}, some intrusion can be detected only after the first package or a few packages are sent, which is capable to reduce the time cost even more.
+So extracting more package based features for model training can be considered as another improvement.
 \end{itemize}
@@
 \section{Conclusion}\label{sec:conclusion}
+In this paper, a new cost-based approach for fast intrusion detection is proposed.
+Utilizing both decision tree models and neural network models with GPU acceleration, the proposed IDS is capable of maintaining high detecting intrusion accuracy with the minimization of both computational cost and time cost.
+The results are evaluated on NSL-KDD dataset, and a good performance is demonstrated in the experiments.
+
+However, there still remains many issues to be solved for IDSs, such as how to detect intrusion only after a few packages have been received, and how to accurately detect zero-day attacks.
+Further research will investigate to solve the mentioned issues.
 

### 2017-06-05 baseline.py

@@ -3,18 +3,19 @@ from sklearn import svm
 from process_data import znormalization
 import time
 
-data = np.load('./feature/tcp_finger.npz')
+data = np.load('./feature/icmp_eco_i.npz')
+opt = 39
 
-x_train = data['x_train'][:,0:7]
+x_train = data['x_train'][:,0:opt]
 y_train = data['y_train'].ravel()
-x_test = data['x_test'][:,0:7]
+x_test = data['x_test'][:,0:opt]
 y_test = data['y_test'].ravel()
 
 X_train = znormalization(x_train)
 X_test = znormalization(x_test)
 X_train = np.nan_to_num(X_train)
 X_test = np.nan_to_num(X_test)
-
+print X_train
 clf = svm.SVC()
 clf.fit(X_train, y_train)
 
@@ -22,4 +23,11 @@ time1 = time.time()
 result = np.round(clf.predict(X_test))
 time2 = time.time()
 print float(time2 - time1) / float(len(y_test))
-print float(sum(result==y_test)) / float(len(y_test))
+#print float(sum(result==y_test)) / float(len(y_test))
+
+fp = 0
+for i in range(len(y_test)):
+	if y_test[i] == 0 and result[i] == 1:
+		fp = fp + 1
+
+print float(fp) / float(sum(y_test==0))

### 2017-06-05 baseline_all.py

@@ -5,10 +5,11 @@ import time
 
 train = np.load('./feature/train.npz')
 test = np.load('./feature/test.npz')
+opt = 22
 
-x_train = train['feature'][:,0:7]
+x_train = train['feature'][:,0:opt]
 y_train = train['label_2'].ravel()
-x_test = test['feature'][:,0:7]
+x_test = test['feature'][:,0:opt]
 y_test = test['label_2'].ravel()
 
 X_train = znormalization(x_train)
@@ -23,4 +24,11 @@ time1 = time.time()
 result = np.round(clf.predict(X_test))
 time2 = time.time()
 print float(time2 - time1) / float(len(y_test))
-print float(sum(result==y_test)) / float(len(y_test))
+#print float(sum(result==y_test)) / float(len(y_test))
+
+fp = 0
+for i in range(len(y_test)):
+	if y_test[i] == 0 and result[i] == 1:
+		fp = fp + 1
+
+print float(fp) / float(sum(y_test==0))

### 2017-06-05 train_nn.py

@@ -6,7 +6,7 @@ import time
 
 train = np.load('./feature/train.npz')
 test = np.load('./feature/test.npz')
-opt = 41
+opt = 22
 
 X_train = train['feature'][:,0:opt]
 label_2 = train['label_2']
@@ -33,6 +33,7 @@ b_fc2 = bias_variable([2])
 h_fc2 = tf.nn.tanh(tf.matmul(h_fc1, W_fc2) + b_fc2)
 
 y_logits = h_fc2
+result = tf.argmax(y_logits, 1)
 
 cross_entropy = tf.reduce_mean(
     tf.nn.softmax_cross_entropy_with_logits(y_logits, y))
@@ -70,10 +71,18 @@ for epoch_i in range(n_epochs):
 
         sess.run(optimizer, feed_dict={
             x: batch_xs, y: batch_ys, keep_prob: 0.75})
-    time1 = time.time()
-    print('test (%d): ' % epoch_i + str(sess.run(accuracy,feed_dict={x: X_test,y: Y_test,keep_prob: 1.0})))
-    time2 = time.time()
-    time_sum = time_sum + float(time2 - time1) / float(len(y_test))
+    #time1 = time.time()
+	acc = sess.run(accuracy,feed_dict={x: X_test,y: Y_test,keep_prob: 1.0})
+    print('test (%d): ' % epoch_i + str(acc))
+    #time2 = time.time()
+    #time_sum = time_sum + float(time2 - time1) / float(len(y_test))
     # grad_vals = sess.run([g for (g,v) in grads], feed_dict={x: batch_xs, y: batch_ys, keep_prob: 1.0})
     # print 'grad_vals: ', grad_vals
+    if acc > 0.75:
+        fp = 0
+        predict = sess.run(result,feed_dict={x: X_test,y: Y_test,keep_prob: 1.0})
+        for i in range(len(predict)):
+            if y_test[i] == 0 and predict[i] == 1:
+                fp = fp + 1
+        print float(fp) / float(sum(y_test==0))
 print time_sum / 1000

### 2017-06-05 tex/paper_v1.tex
add false alarm

@@
 
-As observed, the false alarm rates decay as the increasing level of features.
+As observed, the false alarm rates tends to decay as the increasing level of features.
+Especially, for the ICMP eco\_i models, the false alarm rates decay significantly for Level 3 features.
+For these type of situations, the extraction of high level features is necessary.
 
@@
 SVM & $3.86\%$ & $0.00\%$ & $0.67\%$ & $57.69\%$ \tabularnewline
-Ours & $4.40\%$ & $99.26\%$ & $99.33\%$ & $94.27\%$\tabularnewline
+Ours & $4.40\%$ & $0.00\%$ & $0.67\%$ & $57.69\%$\tabularnewline
 \hline
@@
 
-SVM & $81.39\%$ & $0.00\%$ & $0.45\%$ & $57.69\%$\tabularnewline
-Ours & $3.49\%$ & $99.26\%$ & $99.78\%$ & $94.27\%$\tabularnewline
+SVM & $1.81\%$ & $0.00\%$ & $0.45\%$ & $57.69\%$\tabularnewline
+Ours & $3.49\%$ & $0.00\%$ & $0.45\%$ & $57.69\%$\tabularnewline
 \hline
@@
 SVM & $2.19\%$ & $0.00\%$ & $0.00\%$ & $19.23\%$\tabularnewline
-Ours & $6.64\%$ & $99.26\%$ & $99.78\%$ & $98.89\%$\tabularnewline
+Ours & $6.64\%$ & $0.00\%$ & $0.00\%$ & $7.69\%$\tabularnewline
 \hline

### 2017-06-05 train_example.py

@@ -35,6 +35,7 @@ b_fc2 = bias_variable([2])
 h_fc2 = tf.nn.tanh(tf.matmul(h_fc1_drop, W_fc2) + b_fc2)
 
 y_logits = h_fc2
+result = tf.argmax(y_logits, 1)
 
 cross_entropy = tf.reduce_mean(
     tf.nn.softmax_cross_entropy_with_logits(y_logits, y))
@@ -72,12 +73,18 @@ for epoch_i in range(n_epochs):
 
         sess.run(optimizer, feed_dict={
             x: batch_xs, y: batch_ys, keep_prob: 0.75})
-    time1 = time.time()
-    print('test (%d): ' % epoch_i + str(sess.run(accuracy,feed_dict={x: X_test,y: Y_test,keep_prob: 1.0})))
-    time2 = time.time()
-    time_sum = time_sum + float(time2 - time1) / float(len(y_test))
+    #time1 = time.time()
+    acc = sess.run(accuracy,feed_dict={x: X_test,y: Y_test,keep_prob: 1.0})
+    print('test (%d): ' % epoch_i + str(acc))
+    #time2 = time.time()
+    #time_sum = time_sum + float(time2 - time1) / float(len(y_test))
     # grad_vals = sess.run([g for (g,v) in grads], feed_dict={x: batch_xs, y: batch_ys, keep_prob: 1.0})
     # print 'grad_vals: ', grad_vals
-    # theta = sess.run(h_fc1, feed_dict={x: batch_xs, keep_prob: 1.0})
-    # print theta
+    if acc > 0.98:
+        fp = 0
+        predict = sess.run(result,feed_dict={x: X_test,y: Y_test,keep_prob: 1.0})
+        for i in range(len(predict)):
+            if y_test[i] == 0 and predict[i] == 1:
+                fp = fp + 1
+        print float(fp) / float(sum(y_test==0))
 print time_sum/n_epochs

### 2017-06-05 tex/paper_v1.tex
>>-.-<<

@@
 
-This work aims at reduce the features used for misuse-based techniques\cite{chebrolu2005feature}, since the comparison between the whole packet and all the signatures can be redundant.
+This work\cite{chebrolu2005feature} aims at reduce the features used for misuse-based techniques, since the comparison between the whole packet and all the signatures can be redundant.
 And useful feature selection algorithms are proposed.
@@
 
-Ensemble learning is extensively used in intrusion detection\cite{zhang2008random}\cite{mukkamala2005intrusion}. The single model can be nearly all kinds of previous mentioned machine learning models.
+Ensemble learning methods are extensively utilized in intrusion detection\cite{zhang2008random}\cite{mukkamala2005intrusion}.
+The single model can be nearly all kinds of previous mentioned machine learning models.
+
+\vspace{6pt}
+
+In the approach proposed in this paper, both the supervised learning and ensemble learning methods are employed, namely, the decision tree model and the neural networks model.
+Empirically, this combination demonstrates a great improvement compared with using single model for prediction.
 
@@
 Different from\cite{lee2001real}, the connection based features are utilized according to\cite{lee2001real} in this paper.
+The exact levels of features are presented in Tab \ref{tab:feature}.
 
@@
 \end{itemize}
+
+\begin{table*}
+
+\caption{\label{tab:feature}Levels of Features.}
+\centering{}
+\begin{tabular}{c|c|c}
+
+\hline 
+Level 1 Features & Level 2 Features & Level 3 Features\tabularnewline
+\hline
+Duration & Hot & Count \tabularnewline
+Protocol type & Num failed logins & Serror rate \tabularnewline
+Service & Logged in & Rerror rate \tabularnewline
+Src bytes & Num compromised & Same srv rate \tabularnewline
+Dst bytes & Root sell & Diff srv rate \tabularnewline
+Flag & Su attempted & Srv count \tabularnewline
+Land & Num root & Srv serror rate \tabularnewline
+Wrong fragment & Num file creations & Srv rerror rate \tabularnewline
+Urgent & Num shells & Srv diff host rate \tabularnewline
+ & Num access files &  \tabularnewline
+ & Num outbound cmds &  \tabularnewline
+ & Is hot login &  \tabularnewline
+ & Is guest login &  \tabularnewline
+\hline
+
+\end{tabular}
+\end{table*}
 
@@
 Actually due to the less complexity for packets detection, neural network models perform nearly the same as traditional classifiers.
-The main reason of utilizing neural network models in this paper is the excellent CPU acceleration support for deep learning libraries, which will reduce the computational cost in some extent.
+The main reason of utilizing neural network models in this paper is the excellent GPU acceleration support for deep learning libraries, which will reduce the computational cost in some extent.
 
 Neural network models with only one hidden layer is utilized in this paper, and the following experiments proves their capability for intrusion detection with such simple architectures.
+
+\subsection{Evaluation Methods}
+Three evaluation metrics are employed in this paper to evaluate the performance of the intrusion detection system, namely, detection accuracy, false alarm rate and total cost:
+
+\begin{itemize}
+\item Detection accuracy is simply calculated by comparing the predicted results with the ground truth labels.
+\item The false alarm rate(FAR) is defined as Eq \ref{eq:false-alarm}, in which $FP, TN$ represent false positive and true negative samples respectively.
+
+\begin{equation}\label{eq:false-alarm}
+FAR = \frac{FP}{FP+TN}
+\end{equation}
+
+\item The total cost is the sum of the computational cost and the time cost. 
+\end{itemize}
 
@@
 
-Thanks to CPU acceleration, it can be noticed that significant improvement have been made on computational cost utilizing neural network models, which is quite important in real time detection for the IDSs.
+Thanks to GPU acceleration, it can be noticed that significant improvement have been made on computational cost utilizing neural network models, which is quite important in real time detection for the IDSs.
 Also the number of neurons in the hidden layer is reduced as small as possible, which also save the computational cost.
@@
 
-However, there still remains many issues to be solved for IDSs, such as how to detect intrusion only after a few packages have been received, and how to accurately detect zero-day attacks.
-Further research will investigate to solve the mentioned issues.
+However, as mentioned in Sec \ref{sec:futurework}, there still remains many issues to be solved for IDSs, such as how to detect intrusion only after a few packages have been received, and how to accurately detect zero-day attacks.
+Also, more attack simulations need to be organized to test the IDSs before they are actually employed in the real environment, since any crash in IDSs may leads to severe network problems.
+
+After accomplishing the rest experiments, further research will focus on solving the mentioned issues in Sec \ref{sec:futurework}.
 

### 2017-06-05 tex/paper_v1.tex
change overview

@@
 
-In the approach proposed in this paper, both the supervised learning and ensemble learning methods are employed, namely, the decision tree model and the neural networks model.
-Empirically, this combination demonstrates a great improvement compared with using single model for prediction.
+In the approach proposed in this paper, both the supervised learning and ensemble learning methods are employed.
+The combination of decision tree model and neural networks model demonstrates a great improvement compared with using single model for prediction in NSL-KDD dataset.
 
@@
 
+\subsubsection{UNB ISCX 2012 Intrusion Detection Evaluation Dataset}
+This dataset is proposed in \cite{shiravi2012toward}.
+According to \cite{shiravi2012toward}, this labeled dataset consists of realistic network and traffic with complete capture.
+Also, diverse intrusion scenarios are included.
+This dataset demonstrate a good performance in the comparison with other existing datasets.
+
 \section{Methodology}\label{sec:methodology}
@@
 \begin{centering}
-\includegraphics[scale=0.55]{img/overview}
+\includegraphics[scale=0.55]{img/overview-new}
 \par\end{centering}
@@
 
-As shown in Fig \ref{fig:overview}, the decision has very simple architecture in the proposed approach.
+As shown in Fig \ref{fig:overview}, the decision tree has very simple architecture in the proposed approach.
 
@@
 
-\subsubsection{Detection Accuracy.}
+\subsubsection{Detection Accuracy}
 Tab \ref{tab:detection-accuracy} demonstrates the detection accuracy for each level of features.
@@
 
-\subsubsection{False Alarm Rates.}
+\subsubsection{False Alarm Rates}
 Tab \ref{tab:detection-false-alarm} demonstrates the false alarm rates for each level of features. As mentioned before, three representative protocol type and service are presented.
@@
 
-\caption{\label{tab:detection-false-alarm}Detection False Alarm Rates.}
+\caption{\label{tab:detection-false-alarm}Detection False Alarm Rates}
 \centering{}
@@
 \item Try more specific detection results than just normal and anomaly classification. Actually, the NSL-KDD dataset provides the labels of the specific attack types for each connection.
+\item The experiments are originally planned to conducted on the UNB ISCX IDS 2012 dataset, which is the up-to-date dataset for intrusion detection.
+However, it may take months to get the dataset following the procedures on the official website.
+But still, more experiments should be conducted on this new dataset before making any conclusions.
 \end{itemize}
@@
 So extracting more package based features for model training can be considered as another improvement.
+\item The datasets that are extensively used currently are still the simulations two decades ago, which makes the models analyzed in these papers unsuitable for detecting newly appeared attacks in recent years.
+So more datasets are urgently needed in the field of intrusion detection.
 \end{itemize}

### 2017-06-05 split_data.py

@@ -10,7 +10,8 @@ def split_data(url, tcp_finger, label_2):
 	while line:
 		line = line.split(',')
 		temp = str(line[1]) + '_' + str(line[2]) 
-		
+		if not package.has_key(temp):
+			package[temp] = 1
 		if temp == 'icmp_eco_i':
 			line[3] = flag[line[3]]
 			tcp_finger[i,0] = line[0]
@@ -21,7 +22,7 @@ def split_data(url, tcp_finger, label_2):
 				label_2[0, i] = 1
 			i = i + 1
 		line = f.readline()
-	print i
+	print sorted(package)
 	return tcp_finger, label_2
 
 if __name__ == '__main__':
@@ -35,4 +36,4 @@ if __name__ == '__main__':
 	url = './NSL_KDD/KDDTest+.txt'
 	tcp_finger_test, label_2_test = split_data(url, tcp_finger_test, label_2_test)
 	
-	np.savez('./feature/icmp_eco_i.npz', x_train=tcp_finger_train, x_test=tcp_finger_test, y_train=label_2_train, y_test=label_2_test)
+	#np.savez('./feature/icmp_eco_i.npz', x_train=tcp_finger_train, x_test=tcp_finger_test, y_train=label_2_train, y_test=label_2_test)

### 2017-06-05 tex/paper_v1.tex
more related work

@@
 \section{Related Work}\label{sec:relatedwork}
+\subsection{Intrusion Types}
+According to KDD Cup 1999 dataset\cite{tavallaee2009detailed}, all the simulated attacks are classified into four categories:
+
+\begin{itemize}
+\item \textbf{Denial of Service Attack (DoS):} This type of attack aims at making the target computer's service unavailable to its legitimate users by increasing the number of significant resource demanding process to exhaust the target's network bandwidth , CPU load, memory and etc\cite{bhuyan2014detecting}.
+However, with the development of detection and IP tracking techniques, old single source attacks can be easily detected and the source can be rebuffed or shut down.
+A distributed Dos(DDos) attack attack technique has been developed, which is very difficult to defend.
+This survey\cite{zargar2013survey} is highly recommended for more information.
+\item \textbf{User to Root Attack (U2R)} This type of attack refer to the behavior that the attackers trying to gain root access in the system.
+Usually the attacker entrance the system as a normal user first and try to exploit some vulnerabilities in the system.
+\item \textbf{Remote to Local Attack (R2L):} This type of attacks occurs when an attacker send packets to a remote server where the attacker have no legitimate accounts over a network to gain local access as a legitimate user\cite{mukkamala2005intrusion}.
+Usually, this illegal accesses are gained by exploiting vulnerabilities of the server by the attackers.
+\item \textbf{Probing Attack:} This type of attacks are basically an information collection behavior. The attacker scans the computers in a network to gather information or to exploit vulnerabilities.
+For IDSs specially designed for probing attacks, this work \cite{zargar2009identification} is recommended.
+\end{itemize}
+
 \subsection{Detection Methodology}
@@
 Nearly all the former techniques in supervised learning are used in intrusion detection\cite{ingre2015performance}\cite{sommer2010outside}\cite{qiao2002anomaly}.
-Both the computational complexity and concrete introduction of the former techniques can be found in this work\cite{buczak2016survey}.
+Both the computational complexity and concrete introduction of the former techniques can be found in \cite{buczak2016survey} and \cite{tsai2009intrusion}.
 
@@
 
-\caption{\label{tab:feature}Levels of Features.}
+\caption{\label{tab:feature}Features in Different Levels.}
 \centering{}
@@
 And the following baseline results are evaluated on the same server with the proposed approach without GPU support for SVM method.
+Also, empirically, the SVM models are also combined with the same decision tree model in the proposed approach to accomplish a comparative result.
 

### 2017-06-05 tex/paper_v1.tex
final version

--- 2017-06-05 tex/paper_v1.tex
@@
 
-The aim of Intrusion Detection System(IDS) is to maximize detection accuracy as well as minimize corresponding costs.
-In this paper, I present a cost-based approach utilizing neural network with GPU acceleration for fast intrusion detection.
-In this approach, both computational cost and time cost are considered, and models are trained with respect to their different protocol types and services.
+The aim of real time Intrusion Detection Systems(IDSs) is to maximize detection accuracy as well as minimize corresponding costs.
+In this paper, I present a cost-based approach utilizing decision tree and neural network models with GPU acceleration for fast intrusion detection.
+In this approach, both computational cost and time cost are considered, and different models are trained with respect to the types of protocols and services.
 Empirical experiments are carried out on off-line benchmark dataset NSL-KDD.
@@
 \section{Introduction}
-With the development of computing and Internet technology, Internet has became an important part of our daily life. However, this popularity has also brought security issues. 
-Intrusion Detection Systems(IDSs) are designed to detect attacks, which help discover, determine, and identify unauthorized use, duplication, alteration, and destruction of information systems\cite{mukkamala2005cyber}.
-Specifically, IDSs are able to monitor intrusions and alert network administrators if necessary.
+With the development of computing and network technology, Internet has became an important part of our daily life. However, this popularity has also brought many security issues. 
+Intrusion Detection Systems(IDSs) are designed to detect attacks.
+Specifically, it helps to discover, determine, and identify unauthorized use, duplication, alteration, and destruction of information systems\cite{mukkamala2005cyber}.
+Additionally, IDSs are able to monitor the system and alert network administrators if necessary.
 
-According to the detectable attacks, there are mainly three types of IDSs: misuse-based, anomaly-based, and hybrid\cite{buczak2016survey}.
-Misuse-based IDSs, which are also called signature-based IDSs are designed to detect known attacks by comparing new packets and the signatures in the database.
-Anomaly-based IDSs aims at modeling the normal network, and anomalies can be detected when happened.
-An attractive property of the anomaly-based IDSs is that they have the ability for detecting zero-day attacks.
+With respect to the types of detectable attacks, there are mainly three types of IDSs: misuse-based, anomaly-based, and hybrid\cite{buczak2016survey} IDS.
+Misuse-based IDSs, which are also called signature-based IDSs are designed to detect known attacks by comparing new packets and the predefined signatures stored in the database.
+Anomaly-based IDSs aims at modeling the normal network, and anomalies can be detected when happened. Hybrid IDSs combine the former two techniques together.
 
-Also with respect for using environment, IDSs can be used in real-time environment or off-line environment.
-Off-line IDSs have been studied extensively recently especially with the support of data mining and machine learning techniques, such as K-means\cite{lin2015cann} and ANN\cite{ingre2015performance} etc.
-And excellent detection results with high accuracies and low false alarm rates are demonstrated.
-For detailed introduction for these machine learning techniques, the survey\cite{buczak2016survey} is recommended.
+Also with respect to the using environment, IDSs can be divided as the ones used in real-time environment or used in off-line environment.
+Off-line IDSs have been studied extensively recently especially based on data mining and machine learning techniques, such as K-means\cite{lin2015cann} and ANN\cite{ingre2015performance} etc.
+And excellent detection results with high accuracies and low false alarm rates on the off-line datasets are accomplished.
 
-However, these systems fail to provide real time information, which means they can only detect intrusions after they already happened for a while.
-However, it's obvious that as the complexity of features increase, the detection accuracy will also make an improvement.
-So a balance need to be maintained between accuracy and efficiency.
+However, these IDSs always fail to provide real-time detection, which means they can only detect intrusions after the they already happened for a while and are not capable in defending the host from an attack at all.
+This is because the excellent off-line performance is often achieved thanks to the comprehensive extracted features and long time complicated computing.
+So a balance need to be maintained between accuracy and efficiency in real-time IDSs.
 
 In this paper, the aim is to develop an IDS which can be utilized in real-time environment with high detection accuracy and low cost.
-I present a cost-based approach for anomaly intrusion detection.
-The traditional machine learning models are replaced by neural networks, which enable the computational cost to be minimized utilizing GPU acceleration.
+For the minimization of computational cost, I present a cost-based approach for fast intrusion detection.
+The traditional machine learning models are replaced by neural networks, which enable the utilizing of GPU acceleration.
 Also, the time cost is considered, and according to the time cost theory in \cite{lee2001real}, low level features are utilized with high priority.
-The benchmark dataset NSL-KDD is used for evaluation, which is a new version of dataset KDD Cup 1999\cite{cup2007available} and has significant improvements compared with KDD Cup 1999\cite{tavallaee2009detailed}.
+The benchmark dataset NSL-KDD is used as testbed for evaluation, which is a new version of dataset KDD Cup 1999 dataset\cite{cup2007available} and has significant improvements compared with KDD Cup 1999 dataset\cite{tavallaee2009detailed}.
 
@@
 Sec \ref{sec:relatedwork} gives a detailed review of current related work about intrusion detection.
-In Sec \ref{sec:methodology}, the new approach for intrusion detection is introduced.
+In Sec \ref{sec:methodology}, the new approach for intrusion detection is proposed.
 The experimental results are reported in Sec \ref{sec:experiment}.
@@
 \section{Related Work}\label{sec:relatedwork}
+\subsection{Intrusion Types}
+There are many types of intrusions.
+According to KDD Cup 1999 dataset\cite{tavallaee2009detailed}, all the simulated attacks are classified into four categories:
+
+\begin{itemize}
+\item \textbf{Denial of Service Attack (DoS):} This type of attacks aim at making the services of target computer unavailable to its legitimate users by increasing the number of significant resource demanding processes to exhaust the target's network bandwidth , CPU load, or memory etc\cite{bhuyan2014detecting}.
+However, with the development of detection and IP tracking techniques, old single source attacks can be easily detected and the source can be rebuffed or shut down.
+Many kinds of  distributed Dos(DDos) attack techniques have been developed.
+One of the effective approaches to detect DDos attacks is to capture and recognize patterns of the DDos affected traffic\cite{robinson2015ranking}.
+This survey\cite{zargar2013survey} is recommended for more information.
+\item \textbf{User to Root Attack (U2R)} This type of attacks refer to the behavior that the attacker tries to gain root access of the system.
+Usually the attacker enters the system as a normal user first and try to exploit some vulnerabilities in the system to gain illegal root access.
+\item \textbf{Remote to Local Attack (R2L):} This type of attacks occur when an attacker tries to gain local access as a legitimate user on a remote server where actually he or she has no legitimate accounts.
+R2L attacks are often carried out by sending packets over network to the remote server\cite{mukkamala2005intrusion}.
+Usually, this illegal accesses are gained by taking advantages of vulnerabilities on the server.
+\item \textbf{Probing Attack:} This type of attacks are basically an information collection behavior.
+The attacker scans the computers in a specific network to gather information or to exploit vulnerabilities.
+For more information about IDSs specially designed for probing attacks, this work \cite{zargar2009identification} is recommended.
+\end{itemize}
+
 \subsection{Detection Methodology}
-Basically, there are three types of intrusion detection techniques: misuse-based, anomaly-based, and hybrid\cite{buczak2016survey}. Hybrid techniques are a combination for the two former techniques.
+Basically, there are three types of intrusion detection techniques: misuse-based, anomaly-based, and hybrid\cite{buczak2016survey}. In the following parts, a brief introduction is presented.
 
@@
 A signature is a pattern or string that corresponds to a known attack or threat\cite{liao2013intrusion}.
-So in the misuse-based IDS, the process for coming packets is to compare them with the known signatures for recognizing possible intrusions.
+So in the misuse-based IDS, the detection procedure for new coming packets is to compare them with the known signatures for recognizing possible intrusions.
 
-The advantages of misuse-based method is that the misuse-based method is effective for detecting known type of attacks free from false alarms.
-However, the disadvantages are that it's usually hard to keep the signature database up to date.
-Also, the technique is incapable in detecting zero-day attacks or any attacks whose signatures are not included in the database.
+The main advantage of misuse-based methods is that the method is effective for detecting known type of attacks and the detection results are free from false alarms.
+However, there are also some disadvantages.
+Firstly, it's usually hard to keep the signature database up to date.
+Secondly, this type of IDSs are incapable in detecting zero-day attacks or any attacks whose signatures are not included in the database, so their abilities are quite limited.
 
 \subsubsection{Anomaly-based Intrusion Detection}
-An anomaly is a deviation to a known behavior, and profiles represent the normal or expected behaviors derived from monitoring regular activities, network connections, hosts or users over a period of time\cite{liao2013intrusion}.
-The anomaly-based techniques aims at modeling normal network status, and new packets are compared with the normal normal status to distinguish an attack.
+An anomaly is a deviation from a known behavior\cite{liao2013intrusion}.
+The anomaly-based techniques aim at modeling normal status including regular activities, normal network connections, hosts or users etc.
+And new packets different from normal status can be detected, the anomalies are considered to be an attack.
 
-The advantages of anomaly-based method is that they have the ability to recognize zero-day attacks.
-Another advantage is that unlike the misuse-based method, the profiles of normal activity are customized for every system, application, or network, thereby making it difficult for attackers to know which activities they can carry out undetected\cite{buczak2016survey}.
-The main disadvantage of anomaly-based techniques is the it may present high false alarm rates, since every behavior that has not happened before has the potential risk to be considered as a intrusion.
+One of the most attracting advantages of anomaly-based methods is that they have the abilities to recognize zero-day attacks.
+Another advantage is that unlike the misuse-based methods, the profiles of normal activities are customized for every system, application, or network, thereby making it difficult for attackers to know which activities they can carry out undetected\cite{buczak2016survey}.
+The main disadvantage of anomaly-based techniques is the they may present high false alarm rates, since every behavior that has not happened before has the potential risk to be considered as an intrusion by this type of IDSs.
 
 \subsubsection{Hybrid Intrusion Detection}
-Hybrid techniques combine the former two types of methods.
-They are implemented aiming at decrease the false alarm rate as well as detecting zero-day attacks.
+Hybrid techniques combine the former two types of techniques.
+They are implemented aiming at decreasing the false alarm rate as well as detecting zero-day attacks. Actually, pure anomaly-based IDSs are rarely used.
 
-\subsection{Feature Selection}
-The reduction of features and feature selection are very important in increasing the efficiency of the detection.
+\subsection{Feature Selection}\label{sec:feature-selection}
+The reduction of features and feature selection are very important issues in increasing the efficiency of the detection.
 
-This work\cite{chebrolu2005feature} aims at reduce the features used for misuse-based techniques, since the comparison between the whole packet and all the signatures can be redundant.
-And useful feature selection algorithms are proposed.
-Also, the features on one specific dataset KDD Cup 1999 are analyzed by comparing the relevance between each features and information gain is employed to find the most discriminating features for each class\cite{kayacik2005selecting}.
+This work\cite{chebrolu2005feature} aims at reducing the features used for misuse-based techniques, since the comparison between the whole packet and all the signatures can be time demanding and actually redundant.
+Also, useful feature selection algorithms are proposed in the paper.
+Furthermore, the features on one specific dataset KDD Cup 1999 dataset are analyzed by comparing the relevance between each features and information gain is employed to find the most discriminating features for each class\cite{kayacik2005selecting}.
 
-Unsupervised machine learning techniques such as PCA\cite{liu2007hierarchical}\cite{lakhina2010feature} and K-means\cite{kumar2013k} are employed for feature selection.
-And all of these methods demonstrates good performance in feature selection.
+Unsupervised machine learning techniques such as PCA\cite{liu2007hierarchical}\cite{lakhina2010feature} and K-means\cite{kumar2013k} are employed for feature selection process.
+And all of these methods demonstrates good performance on reducing the dimension of features and maintaining only the most representative ones.
 
-However, these feature selection method ignore the time cost brought by the extraction process, so the selected features may bring severe time delay.
+However, as these feature selection methods are nearly all used in off-line detection, they ignore the time cost brought by the feature extraction process.
+So the selected features may bring severe time delay.
 In the cost-based approach presented in this paper, the cost factors are considerer, and a balance between cost and accuracy is maintained.
@@
 \subsection{Machine Learning Approaches}
-In this section present a brief introduce of the utilization of machine learning techniques in intrusion detection.
-Specific machine learning algorithm is beyond the scope of this paper, and this book\cite{bishop2006pattern} is highly recommended for more information.
+In this section, I present a brief introduce of the utilization of machine learning techniques in intrusion detection.
+Specific machine learning algorithms are beyond the scope of this paper, and this book\cite{bishop2006pattern} is highly recommended for more knowledge on pattern recognition machine learning.
 
 \subsubsection{Supervised Learning}
-Supervised learning can be divided into generative models and deterministic models, and both contain plenty of proposed models.
+Supervised learning can be divided into generative models and deterministic models, and both classes contain plenty of proposed models.
 Some of the popular supervised learning methods are listed as follows: Artificial Neural Network, Bayesian Network, Decision Tree, Genetic Algorithms, Hidden Markov Models, Naive Bayes, Support Vector Machine etc.
 
-Nearly all the former techniques in supervised learning are used in intrusion detection\cite{ingre2015performance}\cite{sommer2010outside}\cite{qiao2002anomaly}.
-Both the computational complexity and concrete introduction of the former techniques can be found in this work\cite{buczak2016survey}.
+Nearly all the mentioned techniques in supervised learning are used in intrusion detection, only a few papers are listed here\cite{ingre2015performance}\cite{sommer2010outside}\cite{qiao2002anomaly}.
+Comprehensive computational complexity analysis and concrete introduction of the supervised machine learning techniques can be found in \cite{buczak2016survey} and \cite{tsai2009intrusion}.
 
 \subsubsection{Unsupervised Learning}
-One of the most frequently used techniques is \textbf{clustering}.  
-It is an unsupervised learning aims at clustering the data with some same property together.
+One of the most frequently used unsupervised learning techniques is \textbf{clustering}.  
+This method aims at clustering the data with some similar properties together.
 The main advantage of clustering is that it makes the labeling work not necessary.
-Specifically, for intrusion detection, the system can learn from audit data without requiring the network administrator to provide the attacks information.
+Specifically, for intrusion detection task, this type of IDS can learn from audit data without labeling or requiring the network administrator to provide concrete attacks' information.
 
-There are many clustering method that demonstrates an excellent performance in detection intrusion experiments\cite{hendry2008intrusion}\cite{lin2015cann}\cite{kumar2013k}\cite{tsai2010triangle}.
-K-means, K-NN and etc are popular unsupervised machine learning approaches.
-Also, some work combine them together and better results are demonstrated\cite{lin2015cann}.
-However, as mentioned in the mentioned work, feature selection and reduction are urgently needed in methods like K-NN, because computing the similarities between high dimensions of features are expensive.
+There are many clustering methods that demonstrate excellent performance in the evaluation\cite{hendry2008intrusion}\cite{lin2015cann}\cite{kumar2013k}\cite{tsai2010triangle}.
+K-means, K-NN are the most frequently used unsupervised learning approaches.
+Also, some work combine K-means and K-NN together and better results are achieved\cite{lin2015cann}.
+However, as mentioned in Sec \ref{sec:feature-selection}, feature selection and reduction are urgently needed in methods like K-NN, because computing the similarities between high dimensional features are really expensive.
 
@@
 Actually, the ensemble learning approaches do not belong to supervised or unsupervised learning.
-Usually, the idea of ensemble learning is to use multiple weak models to build a strong model, since some classification tasks may be difficult for one classifier.
-And complex models with lots of parameters always tend to over fit on the training data.
-Bagging and boosting are frequently used approaches in ensemble learning, \cite{dietterich2000experimental} gives a good example for utilizing ensemble learning methods in decision tree models.
+Basically, the idea of ensemble learning is to use multiple weak models to build a strong model.
+This is because trying to solve some complicated tasks with a single model may lead the model to be extremely complex.
+And it is known that complex models with lots of parameters usually tend to over fit on the training data.
+Bagging and boosting are frequently used approaches in ensemble learning, this work\cite{dietterich2000experimental} gives a good example for utilizing ensemble learning methods in decision tree models.
 
-\textbf{Bagging}\cite{breiman1996bagging} predictors is a method for generating multiple versions of a single model and using these to get an aggregated predictor.
+\textbf{Bagging}\cite{breiman1996bagging} is a method of generating multiple versions of a single model and using them to get an aggregated model.
 The aggregation averages over all the versions of models when predicting a result by majority voting.
-\textbf{Boosting}\cite{freund1995desicion} basically concentrates more the mis-classified data in the modeling process.
-Adaptive Boosting (AdaBoost)\cite{polikar2006ensemble} is one of the most popular algorithms in boosting.
-The \textbf{Random Forest}\cite{breiman2001random} another method that combines the decision trees and ensemble learning. The so-called forest is composed of many decision trees.
+\textbf{Boosting}\cite{freund1995desicion} is based on the idea to concentrate more the mis-classified data of every epoch in the training process.
+Adaptive Boosting (AdaBoost)\cite{polikar2006ensemble} is one of the most frequently used algorithms in boosting.
+The \textbf{Random Forest}\cite{breiman2001random} is a method that combines the decision trees and ensemble learning.
+The so-called forest is composed of many decision trees.
+Also, bagging techniques are employed to avoid over fitting.
+The random forest has been proved to be effective in many tasks.
 
 Ensemble learning methods are extensively utilized in intrusion detection\cite{zhang2008random}\cite{mukkamala2005intrusion}.
-The single model can be nearly all kinds of previous mentioned machine learning models.
+The type of single models used for the aggregation can be nearly all kinds of previous mentioned machine learning models.
 
@@
 The combination of decision tree model and neural networks model demonstrates a great improvement compared with using single model for prediction in NSL-KDD dataset.
+For example, random forest is used both in mis-use based IDS\cite{gharibian2007comparative} and anomaly-based IDS\cite{zhang2008random}.
 
@@
 Totally, seven weeks of training data and two weeks of test data are collected, and attack simulations are organized during both of the periods.
+Notice that for anomaly detection, there are some types of attacks only appear in the test data.
 
 \subsubsection{KDD Cup 1999 Dataset}
-KDD Cup 1999 dataset\cite{tavallaee2009detailed} is one of the most widely used intrusion detection datasets, which is created for the KDD Cup challenge in 1999.
-The dataset is based on DARPA 1998 TCP/IP dataset and some basic features are extracted, as well as some more advanced features like some content features within a connection and traffic features computed using a two-second time window.
+KDD Cup 1999 dataset\cite{tavallaee2009detailed} is also one of the most widely used intrusion detection datasets, which is created for the KDD Cup challenge in 1999.
+The dataset is based on DARPA 1998 TCP/IP dataset and some basic features are extracted.
+Also some more advanced features like some content features within a connection and traffic features computed using a two-second time window are computed.
 Totally, $41$ features are extracted for a single connection.
@@
 \subsubsection{NSL-KDD Dataset}
-As suggested in \cite{tavallaee2009detailed}, the original KDD Cup 1999 dataset has two important issues which highly affects the performance of evaluated systems, and results in a very poor evaluation of anomaly detection approaches.
-The NSL-KDD dataset consists of selected records of the complete KDD data set and free from the mentioned shortcomings in \cite{tavallaee2009detailed}.
+As suggested in \cite{tavallaee2009detailed}, the original KDD Cup 1999 dataset has two important issues which highly affects the performance of evaluated systems, and results in a very poor evaluation of anomaly detection approaches.The NSL-KDD dataset consists of only the selected records of the complete KDD Cup 1999 dataset and free from the mentioned shortcomings in \cite{tavallaee2009detailed}.
 
 \subsubsection{ADFA Intrusion Detection Datasets}
-The ADFA Intrusion Detection Datasets cover both Linux and Windows\cite{creech2013generation}. Different from former introduced datasets, ADFA contains raw system call traces. 
+The ADFA Intrusion Detection Datasets contain data both generated from Linux and Windows\cite{creech2013generation} systems.
+Different from former introduced datasets, ADFA contains raw system call traces.
 A new host-based anomaly intrusion detection methodology is evaluated on ADFD\cite{creech2014semantic}, which utilizing discontiguous system call patterns to increase detection rates whilst reducing false alarm rates.
-Also, excellent results are demonstrated.
 
@@
 As shown in Fig \ref{fig:overview}, a multi-model detector is presented here.
-Based on a decision tree structure, different models are used for every kind of packets with different protocol types and services.
-And neural network models are trained for each level of features respectively.
+Different neural network models are used for packets with different protocol types and services based on a decision tree model.
+Additionally, neural network models are trained for each level of features respectively.
 
@@
 \par\end{centering}
-\caption{\label{fig:overview} An overview of the detection framework including the decision tree(top part) and the neural networks(bottom part).
-The total number of models are calculated on NSL-KDD dataset.}
+\caption{\label{fig:overview} An overview of the detection framework including the decision tree model(top part) and the neural network models(bottom part).
+The sequence number of models are counted based on NSL-KDD dataset.}
 \end{figure*}
@@
 \subsubsection{Computational Cost}
-One of the major challenges in real-time IDSs is the computational cost attached with the system.
-For example, the well-known K-nearest Neighbor Classifier\cite{liao2002use} performs well on off-line datasets, but it is not an appropriate detector in real time.
+One of the major challenges for real-time IDSs is the computational cost attached with the detection procedure.
+For example, the well-known K-nearest Neighbor Classifier(KNNC)\cite{liao2002use} performs well on off-line datasets, but it is not an appropriate detector in real time.
 Because the
 KNNC calculates the similarity between the new 
-packet and each packet in the training set to decide the label of the new packet. So KNNC is computationally
-expensive when the incoming number of packets is huge, causing the system to be overloaded.
+packet and every packet in the training set to decide the label of the new packet. So KNNC is computationally
+expensive when the incoming number of packets is huge, and the system may be overloaded.
 
-Traditionally, less features numbers and models with less parameters will lead to low computational cost.
+Traditionally, reducing the dimension of features and number of parameters in detection models will lead to lower computational cost.
 However, this may also result in lower detection accuracy or higher false alarm rate.
-Different from former approaches, utilizing deep neural networks, the computing tasks can be accelerated on GPU\cite{chetlur2014cudnn}.
-Also, the ability to represent any non-linear function in very few hidden layers and hidden neurons make the computational expense even less.
+Different from former approaches, in utilizing deep neural networks, the computing tasks can be accelerated on GPU\cite{chetlur2014cudnn}.
+Also, the ability of neural network models to represent any non-linear function in very few hidden layers and hidden neurons makes the computational expense even less.
 
@@
 
-Notice that the Level 3 features require iteration from the entire former two-second packet set, the time cost is extremely high compares with the lower level of features.
+Notice that the Level 3 features require iteration from the entire former two-second packet set, the time cost is extremely high compared with the lower level of features.
 Also, all the Level 3 features for connections coming at the same time can also be computed at the same time.
@@
 \item If the confidence of the classification is less than a threshold $\theta$, higher level features are extracted and are used combined with other lower level features;
-\item If the extracted feature level is already $3$, then the eventual detection result is made without confidence calculating.
+\item If the extracted feature level has already reached $3$, the eventual detection result is directly made.
 \end{itemize}
@@
 Packets with different protocol types and different services tend to have different signatures to be malicious.
-Thus different detectors should be trained, and for each new packet, its protocol type and service decides which detector to use. This model selection framework can be modeled by a decision tree.
+Thus different detectors should be trained respectively.
+For each new packet, its protocol type and service decides which detector to use.
+This model selection framework is be modeled by a decision tree.
 
-As shown in Fig \ref{fig:overview}, the decision tree has very simple architecture in the proposed approach.
+As shown in Fig \ref{fig:overview}, the decision tree has very intuitive architecture in the proposed approach.
 
@@
 
-Neural network models are at the bottom layer for the detection process, they trained for each protocol type and service respectively.
+Neural network models are at the leaf nodes for the detection tree, they are trained for each protocol type and service respectively.
 Actually due to the less complexity for packets detection, neural network models perform nearly the same as traditional classifiers.
-The main reason of utilizing neural network models in this paper is the excellent GPU acceleration support for deep learning libraries, which will reduce the computational cost in some extent.
+The main reason of utilizing neural network models in this paper is the excellent GPU acceleration support for deep learning libraries, which will reduce the computational cost to some extent.
 
-Neural network models with only one hidden layer is utilized in this paper, and the following experiments proves their capability for intrusion detection with such simple architectures.
+Neural network models with only one hidden layer is utilized in this paper, and the following experiments proves their capability for intrusion detection even if they only have such simple architectures.
 
@@
 \begin{itemize}
-\item Detection accuracy is simply calculated by comparing the predicted results with the ground truth labels.
+\item Detection accuracy is calculated by comparing the predicted results with the ground truth labels.
 \item The false alarm rate(FAR) is defined as Eq \ref{eq:false-alarm}, in which $FP, TN$ represent false positive and true negative samples respectively.
@@
 \subsection{Dataset}
-As mentioned in Sec \ref{sec:publicdatasets}, NSL-KDD dataset consists of the selected records of the KDD Cup 1999 dataset, which is more challenging to detect compared with the original widely used benchmark KDD Cup 1999 dataset.
+As mentioned in Sec \ref{sec:publicdatasets}, NSL-KDD dataset consists of the selected records of the KDD Cup 1999 dataset, which makes it more challenging to be detected compared with the original widely used benchmark KDD Cup 1999 dataset.
 The NLS-KDD dataset solves the issues of models trained on KDD Cup 1999 dataset, which have high seemingly accuracy but actually poor capability of anomaly detection.
@@
 The data preprocessing method z-normalization is employed.
-All the code for the neural network models is implemented in Python utilizing deep learning framework Tensorflow, and the neural network models are trained on one GPU GeForce GTX TITAN X for $5000$ epochs with early stop policy.
-All the neural networks consist of $1$ hidden layer, and the number of hidden neurons are set specifically for every model.
-The initial learning rate is $\eta = 0.0001$ and dropout ratio is $0.75$ to avoid over fitting.
-Finally, a softmax layer is utilized to calculate loss and Adam\cite{kingma2014adam} is employed to accelerate learning.
-The prediction results of the models are the values of the two output neurons.
+All the code for training the neural network models is implemented in Python utilizing deep learning framework Tensorflow, and the neural network models are trained on one GPU GeForce GTX TITAN X for $5000$ epochs with early stop policy.
+All the neural network models consist of $1$ hidden layer, and the number of hidden neurons are set specifically for every model.
+The initial learning rate is $\eta = 0.0001$ and dropout ratio is set to be $0.75$ to avoid over fitting.
+Eventually, a softmax layer is utilized to calculate loss and Adam\cite{kingma2014adam} is employed to accelerate learning.
+The final prediction results of the models are the values of the two output neurons.
 
@@
 Support Vector Machine(SVM) is employed as a baseline method for each model respectively.
-The code are implemented in Python on Scikit-learn Library.
+The code are implemented in Python utilizing Scikit-learn Library.
 And the following baseline results are evaluated on the same server with the proposed approach without GPU support for SVM method.
+Also, empirically, the SVM models are also combined with the same decision tree model in the proposed approach to accomplish a comparative result.
 
@@
 Tab \ref{tab:detection-accuracy} demonstrates the detection accuracy for each level of features.
-And apart from the over all accuracy, I take three representative protocol type and service(TCP finger/UDP domain\_u/ICMP eco\_i) as examples.
+And apart from the over all accuracy, I take three representative protocol types and services(TCP finger/UDP domain\_u/ICMP eco\_i) as examples.
 
 Observed from Tab \ref{tab:detection-accuracy}, we can see that SVM models and neural network models perform nearly the same on most of the detections.
-But neural network models demonstrate a good property on the three examples that as the level of features get higher, the accuracies never decay; while the SVM method present less stability.
-Actually, this property is quite important in the proposed approach, because the accuracy decay on higher feature level will result in some eventual detection results to be wrong.
-Since the results for packets that cannot be classified confidently by the lower feature level models are decided finally by the higher feature level models.
+But neural network models demonstrate a good property on the three examples that as the level of features increases, the accuracies never decay; while the SVM method present less stability.
+Actually, this property is quite important in the proposed approach, because the accuracy decay on higher feature levels will result in some eventual detection results to be wrong.
+Since the results for packets that cannot be classified confidently by the lower feature level models are all finally decided by the Level 3 feature models.
 Also, lots of time cost will be wasted for no improvement in detection accuracy.
 
-Also, we can observe that the decision tree idea that to detect different protocol types and service with different models is quite reasonable.
+Also, we can observe that the idea of utilizing decision tree models to detect different protocol types and service with different models is quite reasonable.
 In Tab \ref{tab:detection-accuracy}, huge accuracy improvement has been made thanks to this separation.
@@
 The same as former experiments, three representative protocol type and service are selected.
-Notice here I report the average time for computing single one packet feature item.
+Here I report the average time for computing single one packet feature item.
 
-Thanks to GPU acceleration, it can be noticed that significant improvement have been made on computational cost utilizing neural network models, which is quite important in real time detection for the IDSs.
-Also the number of neurons in the hidden layer is reduced as small as possible, which also save the computational cost.
+Thanks to GPU acceleration, it can be noticed that significant improvement has been made on computational cost utilizing neural network models, which is quite important in real time detection for the IDSs.
+Also practically, the number of neurons in the hidden layer is reduced as small as possible for each model, which also save the computational cost.
+
+Maybe you could notice that in the SVM method, the computational cost may even decay as the number of feature dimensions increase.
+This is because in the SVM model, only the training data on the decision boundary is used in the calculation for prediction, so the actual computational cost does not only depend on the dimension of features.
+For more theoretical knowledge of SVM, this book\cite{bishop2006pattern} is recommended.
 
 Also, \textbf{time cost} is considered.
-Every new packet are first detected according to their Level 1 features.
+Following the process of utilizing different levels of features, new packet is first detected according to its Level 1 features.
 If the confidence of the classification, which is the larger value of the two output neurons is less than $\theta=0.8$, than the higher features are extracted and higher level models are used.
-In the worst case, the packet will eventually get its label through Level 3 models. And more additional computational cost will also be spent.
+In the worst case, the packet will eventually get its label through Level 3 models. And more additional computational cost will also be spent at the same time.
 
 The total cost is the sum of computational cost and time cost.
-The proposed approach is much more efficient compared with simply using Level 3 features for all the packets, and there is almost no decay of detection accuracy.
+The proposed approach is much more efficient compared with simply using Level 3 features for all the packets.
+Additionally, there is almost no decay of detection accuracies or increment of false alarm rates.
 
@@
 \item Calculate the average performance for all the models, not for only some examples.
-\item Measure the specific improvement made by distinguishing different level of features quantitatively, such as calculate the exact cost saved for detecting some packets.
+\item Measure the specific improvement made by distinguishing different level of features quantitatively, such as calculate the exact cost saved for detecting testing packets.
 \item Try more specific detection results than just normal and anomaly classification. Actually, the NSL-KDD dataset provides the labels of the specific attack types for each connection.
-\item The experiments are originally planned to conducted on the UNB ISCX IDS 2012 dataset, which is the up-to-date dataset for intrusion detection.
-However, it may take months to get the dataset following the procedures on the official website.
+\item The experiments are originally planned to be conducted on the UNB ISCX IDS 2012 dataset, which is the up-to-date dataset for intrusion detection.
+However, it will take months to get the dataset following the procedures on the official website.
 But still, more experiments should be conducted on this new dataset before making any conclusions.
@@
 \begin{itemize}
-\item There are some protocol type and service with very few training data, such as TCP pm\_dump, UDP tftp\_u and ICMP urh\_i etc.
-This issue will make it impossible to train a neural network model.
-Maybe some signature-based technique are needed here.
-\item It will cost too much time to train and tune parameters for every model, specifically $72$ models in NSL-KDD dataset. But currently I just train the example models manually.
-\item Utilizing the features in NSL-KDD makes the detection in this paper to be connection based, which means that the intrusion can only be detected after all the packages in one connection have arrived.
-Actually, as suggested in\cite{lee2001real}, some intrusion can be detected only after the first package or a few packages are sent, which is capable to reduce the time cost even more.
-So extracting more package based features for model training can be considered as another improvement.
+\item There are some protocol types and services with very few training data, such as TCP pm\_dump, UDP tftp\_u and ICMP urh\_i etc.
+Such a small training dataset will make it impossible to train a neural network model.
+Maybe some signature-based technique are needed for these services.
+\item It will cost too much time to train and tune parameters for every model, specifically $72$ models in NSL-KDD dataset.
+But currently I just train the example models manually because the number of hidden neurons are set to be customized for every model.
+\item Utilizing the features in NSL-KDD makes the detection in this paper to be connection based, which means that the intrusion can only be detected after all the packets in one connection have arrived.
+Actually, as suggested in\cite{lee2001real}, some intrusion can be detected only after the first packet or only after a few packets have been received, which is capable to reduce the time cost even more.
+So extracting more packet based features for model training can be considered as another improvement.
 \item The datasets that are extensively used currently are still the simulations two decades ago, which makes the models analyzed in these papers unsuitable for detecting newly appeared attacks in recent years.
-So more datasets are urgently needed in the field of intrusion detection.
+So more public datasets are urgently needed in the field of intrusion detection.
 \end{itemize}
@@
 In this paper, a new cost-based approach for fast intrusion detection is proposed.
-Utilizing both decision tree models and neural network models with GPU acceleration, the proposed IDS is capable of maintaining high detecting intrusion accuracy with the minimization of both computational cost and time cost.
-The results are evaluated on NSL-KDD dataset, and a good performance is demonstrated in the experiments.
+Utilizing both decision tree model and neural network models with GPU acceleration, the proposed IDS is capable of maintaining high detection accuracy and low false alarm rate with the minimization of both computational cost and time cost.
+The experiments are carried out on NSL-KDD dataset, and a good performance is demonstrated in the evaluation.
 
-However, as mentioned in Sec \ref{sec:futurework}, there still remains many issues to be solved for IDSs, such as how to detect intrusion only after a few packages have been received, and how to accurately detect zero-day attacks.
-Also, more attack simulations need to be organized to test the IDSs before they are actually employed in the real environment, since any crash in IDSs may leads to severe network problems.
+However, as mentioned in Sec \ref{sec:futurework}, there are still many issues that needed to be solved for developing IDSs, such as how to detect intrusion only after a few packets have been received, or how to accurately detect zero-day attacks.
+Also, more attack simulations need to be organized to test the IDSs before they are actually employed in the real environment, since any crash in IDSs may leads to severe problems.
 

### 2017-06-05 tex/paper_v1.tex
final final version >.<

@@
 The aim of real time Intrusion Detection Systems(IDSs) is to maximize detection accuracy as well as minimize corresponding costs.
-In this paper, I present a cost-based approach utilizing decision tree and neural network models with GPU acceleration for fast intrusion detection.
+In this paper, I present a cost-based approach utilizing decision tree model and neural network models with GPU acceleration for fast intrusion detection.
 In this approach, both computational cost and time cost are considered, and different models are trained with respect to the types of protocols and services.
@@
 Intrusion Detection Systems(IDSs) are designed to detect attacks.
-Specifically, it helps to discover, determine, and identify unauthorized use, duplication, alteration, and destruction of information systems\cite{mukkamala2005cyber}.
+Specifically, they help to discover, determine, and identify unauthorized use, duplication, alteration, and destruction of information systems\cite{mukkamala2005cyber}.
 Additionally, IDSs are able to monitor the system and alert network administrators if necessary.
 
-With respect to the types of detectable attacks, there are mainly three types of IDSs: misuse-based, anomaly-based, and hybrid\cite{buczak2016survey} IDS.
-Misuse-based IDSs, which are also called signature-based IDSs are designed to detect known attacks by comparing new packets and the predefined signatures stored in the database.
+With respect to the types of detectable attacks, there are mainly three types of IDSs: misuse-based, anomaly-based, and hybrid\cite{buczak2016survey} IDSs.
+Misuse-based IDSs, which are also called signature-based IDSs, are designed to detect known attacks by comparing new packets and the predefined signatures stored in the database.
 Anomaly-based IDSs aims at modeling the normal network, and anomalies can be detected when happened. Hybrid IDSs combine the former two techniques together.
@@
 Also with respect to the using environment, IDSs can be divided as the ones used in real-time environment or used in off-line environment.
-Off-line IDSs have been studied extensively recently especially based on data mining and machine learning techniques, such as K-means\cite{lin2015cann} and ANN\cite{ingre2015performance} etc.
+Off-line IDSs have been studied extensively recently especially based on data mining and machine learning techniques, such as K-means\cite{lin2015cann} and ANN\cite{ingre2015performance}.
 And excellent detection results with high accuracies and low false alarm rates on the off-line datasets are accomplished.
 
-However, these IDSs always fail to provide real-time detection, which means they can only detect intrusions after the they already happened for a while and are not capable in defending the host from an attack at all.
-This is because the excellent off-line performance is often achieved thanks to the comprehensive extracted features and long time complicated computing.
+However, these IDSs always fail to provide real-time detection, which means they can only detect intrusions after the they already happened for a while and are not capable of defending the host from attacks at all.
+This is because the excellent off-line performance is often achieved thanks to the comprehensive extracted features and long time complicated computing, which are impossible to get in real-time environment.
 So a balance need to be maintained between accuracy and efficiency in real-time IDSs.
 
-In this paper, the aim is to develop an IDS which can be utilized in real-time environment with high detection accuracy and low cost.
-For the minimization of computational cost, I present a cost-based approach for fast intrusion detection.
-The traditional machine learning models are replaced by neural networks, which enable the utilizing of GPU acceleration.
-Also, the time cost is considered, and according to the time cost theory in \cite{lee2001real}, low level features are utilized with high priority.
-The benchmark dataset NSL-KDD is used as testbed for evaluation, which is a new version of dataset KDD Cup 1999 dataset\cite{cup2007available} and has significant improvements compared with KDD Cup 1999 dataset\cite{tavallaee2009detailed}.
+In this paper, the aim is to develop an IDS which can be utilized in real-time environment with high detection accuracy and low costs.
+For the minimization of computational cost, the traditional machine learning models are replaced by neural network models, which enable the utilizing of GPU acceleration.
+Also, the time cost is considered, and similar with the time cost theory in \cite{lee2001real}, low level features are utilized with high priority.
+The benchmark dataset NSL-KDD is used as testbed for evaluation, which is a new version of KDD Cup 1999 dataset\cite{cup2007available} and significant improvement has been made compared with original KDD Cup 1999 dataset\cite{tavallaee2009detailed}.
 
@@
 \begin{itemize}
-\item \textbf{Denial of Service Attack (DoS):} This type of attacks aim at making the services of target computer unavailable to its legitimate users by increasing the number of significant resource demanding processes to exhaust the target's network bandwidth , CPU load, or memory etc\cite{bhuyan2014detecting}.
+\item \textbf{Denial of Service Attack (DoS):} This type of attacks aim at making the services of target computer unavailable to its legitimate users by increasing the number of resource demanding processes to exhaust the target's network bandwidth , CPU load, or memory etc\cite{bhuyan2014detecting}.
 However, with the development of detection and IP tracking techniques, old single source attacks can be easily detected and the source can be rebuffed or shut down.
-Many kinds of  distributed Dos(DDos) attack techniques have been developed.
+In recent years, many kinds of distributed Dos(DDos) attack techniques have been developed.
 One of the effective approaches to detect DDos attacks is to capture and recognize patterns of the DDos affected traffic\cite{robinson2015ranking}.
@@
 \item \textbf{User to Root Attack (U2R)} This type of attacks refer to the behavior that the attacker tries to gain root access of the system.
-Usually the attacker enters the system as a normal user first and try to exploit some vulnerabilities in the system to gain illegal root access.
+Usually the attacker enters the system as a normal user first and tries to exploit some vulnerabilities in the system to gain illegal root access.
 \item \textbf{Remote to Local Attack (R2L):} This type of attacks occur when an attacker tries to gain local access as a legitimate user on a remote server where actually he or she has no legitimate accounts.
@@
 A signature is a pattern or string that corresponds to a known attack or threat\cite{liao2013intrusion}.
-So in the misuse-based IDS, the detection procedure for new coming packets is to compare them with the known signatures for recognizing possible intrusions.
+So in the misuse-based IDSs, the detection procedure for new coming packets is to compare them with the known signatures to recognize possible intrusions.
 
-The main advantage of misuse-based methods is that the method is effective for detecting known type of attacks and the detection results are free from false alarms.
+The main advantage of misuse-based methods is that the method is effective for detecting known types of attacks and the detection results are free from false alarms.
 However, there are also some disadvantages.
@@
 An anomaly is a deviation from a known behavior\cite{liao2013intrusion}.
-The anomaly-based techniques aim at modeling normal status including regular activities, normal network connections, hosts or users etc.
+The anomaly-based IDSs aim at modeling normal status including regular activities, normal network connections, hosts and users etc.
 And new packets different from normal status can be detected, the anomalies are considered to be an attack.
@@
 \subsection{Feature Selection}\label{sec:feature-selection}
-The reduction of features and feature selection are very important issues in increasing the efficiency of the detection.
+The reduction of features and feature selection are very important issues in increasing the efficiency of intrusion detection.
 
-This work\cite{chebrolu2005feature} aims at reducing the features used for misuse-based techniques, since the comparison between the whole packet and all the signatures can be time demanding and actually redundant.
+This work\cite{chebrolu2005feature} aims at reducing the features used for misuse-based IDSs, since the comparison between the whole packet and all the signatures can be time demanding and actually redundant.
 Also, useful feature selection algorithms are proposed in the paper.
@@
 Unsupervised machine learning techniques such as PCA\cite{liu2007hierarchical}\cite{lakhina2010feature} and K-means\cite{kumar2013k} are employed for feature selection process.
-And all of these methods demonstrates good performance on reducing the dimension of features and maintaining only the most representative ones.
+And all of these methods demonstrate good performance on reducing the dimension of features and reserving only the most representative ones.
 
-However, as these feature selection methods are nearly all used in off-line detection, they ignore the time cost brought by the feature extraction process.
-So the selected features may bring severe time delay.
-In the cost-based approach presented in this paper, the cost factors are considerer, and a balance between cost and accuracy is maintained.
+However, since nearly all of these feature selection methods are used in off-line environment, they ignore the time cost brought by the feature extraction process.
+So the proposed selected features may bring severe time delay.
+In the cost-based approach presented in this paper, the time cost factors are considerer, and a balance between efficiency and accuracy is maintained.
 
@@
 In this section, I present a brief introduce of the utilization of machine learning techniques in intrusion detection.
-Specific machine learning algorithms are beyond the scope of this paper, and this book\cite{bishop2006pattern} is highly recommended for more knowledge on pattern recognition machine learning.
+Specific machine learning algorithms are beyond the scope of this paper, and this book\cite{bishop2006pattern} is highly recommended for more knowledge on pattern recognition and machine learning.
 
 \subsubsection{Supervised Learning}
-Supervised learning can be divided into generative models and deterministic models, and both classes contain plenty of proposed models.
+Supervised learning can be further divided into two classes: generative models and deterministic models.
+Both classes contain plenty of proposed models.
 Some of the popular supervised learning methods are listed as follows: Artificial Neural Network, Bayesian Network, Decision Tree, Genetic Algorithms, Hidden Markov Models, Naive Bayes, Support Vector Machine etc.
@@
 Nearly all the mentioned techniques in supervised learning are used in intrusion detection, only a few papers are listed here\cite{ingre2015performance}\cite{sommer2010outside}\cite{qiao2002anomaly}.
-Comprehensive computational complexity analysis and concrete introduction of the supervised machine learning techniques can be found in \cite{buczak2016survey} and \cite{tsai2009intrusion}.
+Comprehensive computational complexity analysis and concrete introduction results can be found in \cite{buczak2016survey} and \cite{tsai2009intrusion}.
 
@@
 One of the most frequently used unsupervised learning techniques is \textbf{clustering}.  
-This method aims at clustering the data with some similar properties together.
+This method aims at clustering the data with similar properties together.
 The main advantage of clustering is that it makes the labeling work not necessary.
-Specifically, for intrusion detection task, this type of IDS can learn from audit data without labeling or requiring the network administrator to provide concrete attacks' information.
+Specifically, for intrusion detection task, this type of IDS can learn from audit data without labeling or requiring the network administrator to provide concrete information about the attacks.
 
-There are many clustering methods that demonstrate excellent performance in the evaluation\cite{hendry2008intrusion}\cite{lin2015cann}\cite{kumar2013k}\cite{tsai2010triangle}.
+There are many clustering methods that demonstrate excellent performance during evaluation\cite{hendry2008intrusion}\cite{lin2015cann}\cite{kumar2013k}\cite{tsai2010triangle}.
 K-means, K-NN are the most frequently used unsupervised learning approaches.
@@
 Basically, the idea of ensemble learning is to use multiple weak models to build a strong model.
-This is because trying to solve some complicated tasks with a single model may lead the model to be extremely complex.
-And it is known that complex models with lots of parameters usually tend to over fit on the training data.
+This is because trying to solve a complicated task with a single model may lead the model to be extremely complex.
+And it is known that complex models with lots of parameters often tend to over fit on the training data. 
+The aggregation of many weak models can avoid over fitting to some extent.
 Bagging and boosting are frequently used approaches in ensemble learning, this work\cite{dietterich2000experimental} gives a good example for utilizing ensemble learning methods in decision tree models.
@@
 The type of single models used for the aggregation can be nearly all kinds of previous mentioned machine learning models.
+For example, random forest is used both in mis-use based IDS\cite{gharibian2007comparative} and anomaly-based IDS\cite{zhang2008random}.
 
@@
 In the approach proposed in this paper, both the supervised learning and ensemble learning methods are employed.
-The combination of decision tree model and neural networks model demonstrates a great improvement compared with using single model for prediction in NSL-KDD dataset.
-For example, random forest is used both in mis-use based IDS\cite{gharibian2007comparative} and anomaly-based IDS\cite{zhang2008random}.
+The combination of decision tree model and neural networks models demonstrates a great improvement compared with using single model for prediction on NSL-KDD dataset.
 
@@
 Totally, seven weeks of training data and two weeks of test data are collected, and attack simulations are organized during both of the periods.
-Notice that for anomaly detection, there are some types of attacks only appear in the test data.
+Notice that for anomaly detection, there are some types of attacks only appear in the testing data.
 
@@
 \subsubsection{NSL-KDD Dataset}
-As suggested in \cite{tavallaee2009detailed}, the original KDD Cup 1999 dataset has two important issues which highly affects the performance of evaluated systems, and results in a very poor evaluation of anomaly detection approaches.The NSL-KDD dataset consists of only the selected records of the complete KDD Cup 1999 dataset and free from the mentioned shortcomings in \cite{tavallaee2009detailed}.
+As suggested in \cite{tavallaee2009detailed}, the original KDD Cup 1999 dataset has two important shortcomings which highly affect the performance of evaluated systems, and result in a very poor evaluation of anomaly detection approaches.The NSL-KDD dataset consists of only the selected records of the complete KDD Cup 1999 dataset and free from the mentioned issues in \cite{tavallaee2009detailed}.
 
@@
 
-Neural network models are at the leaf nodes for the detection tree, they are trained for each protocol type and service respectively.
+Neural network models are the leaf nodes for the decision tree, they are trained for each protocol type and service respectively.
 Actually due to the less complexity for packets detection, neural network models perform nearly the same as traditional classifiers.
@@
 
-Maybe you could notice that in the SVM method, the computational cost may even decay as the number of feature dimensions increase.
+Maybe you could notice that in the SVM method, the computational cost may even decay as the number of feature dimension increase.
 This is because in the SVM model, only the training data on the decision boundary is used in the calculation for prediction, so the actual computational cost does not only depend on the dimension of features.
